---
title: "April 2022: 30 Day Chart Challenge"
author:
  - name: Clark Sims 
date: "`r Sys.Date()`"
output: distill::distill_article

knit: crsp::knit_html_to_outputs
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  fig.retina = 3,
  fig.path = here::here("exports", "April_2022", "/")
)

pacman::p_load(janitor, pacman, rio, skimr, here, conflicted,
               tidyverse, crsp, gt)

conflict_prefer("clean_names", "janitor")
conflict_prefer("filter", "dplyr")

theme_set(theme_bw(base_size = 15) + theme(legend.position = "bottom"))
```

# **Introduction**

For April I am going to complete some of the [30 Day Chart Challenge](https://github.com/dominicroye/30DayChartChallenge_Edition2022).


# Day 1: Part-to-Whole Comparisons

```{r d1-setup, include = FALSE}
tx_sum <- txhousing %>% 
  group_by(year) %>% 
  mutate(total_sales = sum(sales, na.rm = TRUE)) %>% 
  ungroup() %>% 
  group_by(year, month) %>% 
  mutate(monthly_sales = sum(sales, na.rm = TRUE)) %>% 
  ungroup() %>% 
  distinct(year, month, .keep_all = TRUE) %>% 
  select(year, month, total_sales, monthly_sales) %>% 
  rowwise() %>% 
  mutate(monthly_pct = (monthly_sales / total_sales) * 100) %>% 
  ungroup() %>% 
  mutate(hsize = 2) %>% 
  left_join(tibble(
    month = seq(1:12),
    month_name = month.abb
)) %>% 
  mutate(month_name = factor(month_name, levels = month.abb))


```

```{r d1-chart, include = TRUE}
# tx_sum %>% 
#   group_by(month) %>% 
#   summarize(mean_pct = mean(monthly_pct, na.rm = TRUE)) %>% 
#   mutate(ymax = cumsum(mean_pct),
#          ymin = dplyr::lag(mean_pct, default = 0)) %>% 
#   ggplot(aes(xmin = 3, xmax = 4, ymin = ymax, ymax = ymin, fill = as.factor(month))) + 
#   geom_rect() + 
#   coord_polar(theta = "y") + 
#   xlim(c(2, 4)) + 
#   facet_wrap(~ year)

tx_sum %>% 
  filter(year %in% c(2000, 2008, 2014)) %>%
  ggplot(aes(x = hsize, y = monthly_pct, fill = month_name)) + 
  geom_col(width = 0.2, position = "stack", color = "white", size = 0.25) + 
  coord_polar(theta = "y", direction = -1) +
  xlim(c(1.7, 2.3)) + 
  labs(fill = NULL) + 
  paletteer::scale_fill_paletteer_d("ggthemes::Red_Blue_Brown") +
  facet_wrap(~ year) + 
  theme_void() + 
  labs(title = "Percent of Houses Sold in Texas by Month") + 
  guides(fill = guide_legend(direction = "horizontal", nrow = 1)) + 
  theme(legend.position = "bottom", legend.direction = "horizontal", 
        strip.text = element_text(size = 16, family = "sanserif", color = "#565656"),
        legend.text = element_text(size = 12, color = "#565656"),
        aspect.ratio = 1, 
        plot.title = element_text(size = 24, hjust = 0.5, vjust = 1))



```

# Day 4: Flora Comparisons

```{r d4-setup, include = FALSE}
p_load(rgbif)

sun <- name_suggest(q = 'Helianthus annuus', rank = 'species')$data$key[1]

sun_n <- as.numeric(occ_search(taxonKey = sun)$meta$count)

bes <- name_suggest(q = 'Rudbeckia hirta', rank = 'species')$data$key[1]

bes_n <- as.numeric(occ_search(taxonKey = bes)$meta$count)

flora <- tibble(
  com_name = c("Sunflower", "Blackeyed Susan"),
  sci_name = c("Helianthus annuus", "Rudbeckia hirta"),
  occurences = c(sun_n, bes_n)
)
```

```{r d4-chart, include = TRUE}
flora %>% 
  ggplot(aes(com_name, occurences)) + 
  geom_segment(aes(x = com_name, xend = com_name, y = 0, yend = occurences), color = "#005C55FF") + 
  geom_point(shape = 8, size = 20, color = "yellow") +
  geom_point(size = 6, color = "black") + 
  labs(x = NULL, y = "Number of Occurences", title = "Occurences of Two most common flowers in the United States according to GBIF") + 
  scale_y_continuous(limits = c(0, 100000)) +
  theme(panel.background = element_rect(fill = "#CAD8D8FF"), panel.grid = element_blank(), 
        plot.title.position = "plot", title = element_text(size = 14))
```

# Day 5: Slope Comparisons 

Today I will combine the #30DayChartChallenge with #TidyTuesdayR.

```{r d5-setup, include = FALSE}
p_load(tidytuesdayR)

tt_raw <- tt_load("2022-04-05")

news_orgs <- tt_raw$news_orgs

state_sum <- bind_cols(state.abb, state.name, state.division, state.region) %>% 
  rename("state" = 1, "name" = 2, "division" = 3, "region" = 4)

news_sum <- news_orgs %>% 
  group_by(state, year_founded) %>% 
  filter(state %in% state.abb) %>% 
  count() %>% 
  left_join(state_sum) 

```

```{r d5-plot, include = TRUE}
news_sum %>% 
  filter(str_detect(division, "South Central")) %>% 
  ggplot(aes(year_founded, n, color = name)) + 
  geom_jitter(shape = 18, size = 2) +
  geom_smooth(se = FALSE, method = "lm", size = 0.5, show.legend = FALSE) + 
  paletteer::scale_color_paletteer_d("tidyquant::tq_light", direction = -1) + 
  labs(x = NULL, y = NULL, 
       title = "Number of News Organizations Founded Per Year in the South Central USA", 
       color = NULL) + 
  theme(plot.title.position = "plot", title = element_text(size = 12))

```

# Day 6: Our World in Data Comparisons

```{r d6-setup, include = FALSE}
p_load(owidR, ggtext)

owid_search("education")

ed <- owid("public-education-expenditure-as-share-of-gdp") %>% 
  as_tibble() %>% 
  rename("ed_gdp" = 4) %>% 
  mutate(ed_gdp = ed_gdp / 100)
```

```{r d6-plot, include = TRUE}
ed %>% 
  ggplot(aes(year, ed_gdp, color = entity)) + 
  geom_line(alpha = 0.5) + 
  geom_line(data = ed %>% filter(entity == "United States"), 
            aes(year, ed_gdp), color = "#D62728FF") + 
  scale_x_continuous(labels = seq(from = 1870, to = 2000, by = 25), 
                     breaks = seq(from = 1870, to = 2000, by = 25)) + 
  scale_y_continuous(labels = scales::percent_format()) + 
  geom_point(alpha = 1.5) + 
  paletteer::scale_color_paletteer_d("ggsci::category20_d3", direction = -1) + 
  labs(title = "**Public Spending as a Percentage of GDP**",
       subtitle = "Selected Countries from *1870-1993*", 
       x = NULL, y = NULL, color = NULL) + 
  coord_fixed(ratio = 1000) + 
  theme_light() + 
  theme(plot.title = element_markdown(),
        plot.subtitle = element_markdown(),
        plot.title.position = "plot")
```

# Day 7: Physical Distributions

```{r d7-setup, include = FALSE}
p_load(owidR, rnaturalearth)

# owid_search("terror")

terror <- owid("terrorist-attacks-by-region") %>% 
  clean_names() %>% 
  group_by(code) %>% 
  count()

world <- ne_countries(returnclass = "sf") %>% 
  left_join(terror, by = c("iso_a3" = "code"))
```


```{r d7-plot, include = TRUE}
world %>% 
  ggplot() + 
  geom_sf(aes(fill = n), color = "white", size = 0.1) + 
  paletteer::scale_fill_paletteer_c("grDevices::Fall") +
  lims(x = c(-30, 50), y = c(30, 80)) + 
  theme_void() +
  labs(title = "Number of Terrorist Attack From 1970 - 2017: Europe ") + 
  theme(plot.title.position = "plot")
```

# Day 8: Mountains

```{r d8-setup, include = FALSE}
mtns <- tibble::tribble(
       ~continent,        ~peak,   ~height_m,        ~mountain_range,     ~countries,
         "Africa",       "Kibo", "5895",          "Kilimanjaro",     "Tanzania",
           "Asia",    "Everest", "8848",            "Himalayas", "Nepal, China",
     "Antarctica",     "Vinson", "4892",       "Sentinel Range",            "-",
      "Australia", "Kosciuszko", "2228", "Great Dividing Range",    "Australia",
         "Europe",     "Elbrus", "5642",   "Caucasus Mountains",       "Russia",
  "North America",     "Denali", "6190",         "Alaska Range", "USA (Alaska)",
  "South America",  "Aconcagua", "6962",                "Andes",    "Argentina"
  ) %>% 
  mutate(height_m = parse_number(height_m),
         continent = fct_reorder(continent, height_m),
         sign = paste0(peak, "\n", height_m, "m"))

```

```{r d8-plot, include = TRUE}
mtns %>% 
  ggplot(aes(continent, height_m)) + 
  geom_segment(aes(x = continent, xend = continent,
                   y = 0, yend = height_m)) + 
  geom_label(aes(label = sign), label.r = unit(0.05, "lines")) + 
  scale_y_continuous(limits = c(0, 9000), labels = scales::comma_format(suffix = " m")) + 
  labs(x = NULL, y = NULL)
```


# Day 11: Circular Distributions

```{r d11-setup, include = FALSE}
planets <- tibble::tribble(
          ~planet, ~distance_m, ~size_m,
            "Sun",           "0", 865370,
        "Mercury",    "35000000",   1516,
          "Venus",    "67000000",   3760,
          "Earth",    "93000000",   3959,
           "Mars",   "142000000",   2106,
        "Jupiter",   "484000000",  43441,
         "Saturn",   "889000000",  36184,
         "Uranus",  "1790000000",  15759,
        "Neptune",  "2880000000",  15299
  ) %>% 
  mutate(distance_m = parse_number(distance_m),
         location = sample(1:9, replace = FALSE),
         order = seq(1:9),
         plot_distance = case_when(planet == "Sun" ~ 0,
                                   planet != "Sun" ~ ((865370 / 2) + 
                                                        distance_m + (size_m / 2)) / 10000,
                                   TRUE ~ 0))

```


Not sure why this isn't working, but I'm moving on due to time.

```{r d11-plot, include = TRUE}
planets %>% 
  ggplot(aes(location, plot_distance, color = planet)) + 
  geom_point(aes(size = size_m)) + 
  geom_hline(aes(yintercept = plot_distance), lty = 3, alpha = 0.5) + 
#  scale_y_continuous(limits = c(-1000000000, 3e+09)) + 
  scale_size_area() + 
  coord_polar() + 
  theme_void()
```

# Day 12: Theme Day: *The Economist*

I'm going to work more on Day 11, but use a theme from {ggthemes} based on 
*The Economist* style.

I'm moving on from the solar system. `r emo::ji("sun_with_face")`


```{r d12-plot, include = TRUE}
p_load(ggthemes)

planets %>% 
  ggplot(aes(location, plot_distance, color = planet)) + 
  geom_point() + 
  geom_hline(aes(yintercept = plot_distance), lty = 3, alpha = 0.5) + 
#  scale_y_continuous(limits = c(-1000000000, 3e+09)) + 
  scale_size_area() + 
  coord_polar() + 
  theme_economist()
```



# Day 13: Correlation

I'm going to check out the [{lterdatasampler} package](https://lter.github.io/lterdatasampler/).

```{r d13-setup, include = FALSE}
p_load(lterdatasampler, ggtext)

hbr_maples <- hbr_maples %>% 
  mutate(year = as.factor(year))

```

```{r d13-plot, include = TRUE}
hbr_maples %>% 
  ggplot(aes(stem_length, stem_dry_mass, group = year)) + 
  geom_point(aes(fill = year), shape = 21, show.legend = FALSE) + 
  geom_smooth(aes(color = year), method = "lm", se = FALSE, show.legend = FALSE) + 
  labs(x = "Stem Length (mm)", y = "Stem Mass (g)", 
       title = "The correlation between Stem Mass and Stem Length Differs between <span style = 'color:#624FB0;'>2003</span> and <span style = 'color:#86A556;'>2004</span>.",
       subtitle = "**Sugar Maple Seedlings** in *Hubbard Brook LTER*.",
       caption = "Data Source: **{lterdatasampler}**") + 
  paletteer::scale_fill_paletteer_d("rockthemes::husker", direction = -1) + 
  paletteer::scale_color_paletteer_d("rockthemes::husker", direction = -1) + 
  ggthemes::theme_pander() + 
  theme(legend.title = element_blank(), 
        plot.title.position = "plot", 
        plot.title = element_markdown(), 
        plot.subtitle = element_markdown(size = 10), 
        plot.caption = element_markdown())
```


# Day 14: 3D Relationship

Didn't have time to complete. May revisit.

```{r d14-setup, include = FALSE}

```

# Day 15: Multivariate Relationship

```{r d15-setup, include = FALSE}
p_load(ggtext, ggrepel, paletteer)

msleep2 <- msleep %>% 
  mutate(brain_body = brainwt / bodywt)
```

```{r d15-plot, include = TRUE}
msleep2 %>%
  filter(conservation == "domesticated") %>%
  ggplot(aes(sleep_total, brain_body, color = vore)) + 
  geom_point(shape = 18, size = 3) + 
  geom_smooth(method = "lm", se = FALSE) +
  geom_text_repel(aes(label = name), color = "black", min.segment.length = 0.2) +
  scale_color_paletteer_d("dutchmasters::staalmeesters", direction = -1) + 
  labs(title = "Relationship between **Brain Weight Ratio** and **Total Sleep** in Domesticated Animals: <span style = 'color:#D39C7B;'>Carnivores</span>, <span style = 'color:#060A0D;'>Herbivores</span>, and <span style = 'color:#D7E1D6;'>Omnivores</span>",
       x = "Total Sleep", 
       y = "Brain Weight / Body Weight", 
       caption = "Data Source: {ggplot2::msleep}") +
  theme(legend.position = "none", 
        plot.title = element_textbox_simple(), plot.title.position = "plot",
        plot.caption = element_markdown())
  
```


# Day 18: [OECD](https://data.oecd.org/) Data

```{r d18-setup, include = FALSE}
p_load(OECD, countrycode)

# dataset_list <- get_datasets()
# search_dataset("Health", data = dataset_list) %>% view()

health <- get_dataset(dataset = "HEALTH_LVNG") %>% 
  clean_names()

smoking <- health %>% 
  filter(var == "TOBATBCT", 
         unit %in% c("PDLSFMTF", "PDLSHOTH", "PDLSTOTX")) %>% 
  mutate(country = countrycode(cou, origin = "iso3c", destination = "country.name"),
         flag = countrycode(country, "country.name", "unicode.symbol"))  %>% 
  mutate(group = case_when(unit == "PDLSTOTX" ~ "Total", 
                           unit == "PDLSFMTF" ~ "Women",
                           unit == "PDLSHOTH" ~ "Men"),
         percent_pop = parse_number(obs_value),
         time = parse_number(time))

```

```{r d18-table, include = FALSE}
p_load(gt, gtExtras)

smoking_2019 <- smoking %>% 
  select(country, time, group, percent_pop, flag) %>% 
  filter(time == 2019)


smoking_2019 %>% gt()


```

# Day 19 and 21: Global Change/Down

I'm going to continue with the Day 18 OECD data.

```{r d19-setup, include = FALSE}
smk_19_w <- smoking_2019 %>% 
  pivot_wider(names_from = group, values_from = percent_pop) %>% 
  select(-time) %>% 
  arrange(-Total)
```


```{r d19-gt, include = TRUE}
smoking %>% 
  group_by(country, group) %>% 
  summarize(smk_data = list(percent_pop), .groups = "drop") %>% 
  left_join(smk_19_w) %>% 
  filter(group == "Total", 
         !is.na(Total)) %>% 
  select(-group) %>% 
  rename(Country = country, Trend = smk_data) %>% 
  relocate(Trend, .after = Total) %>% 
  arrange(-Total) %>% 
  gt() %>% 
  gt_merge_stack(Country, flag) %>% 
  tab_spanner(columns = c("Women", "Men", "Total"), label = "2019 Smoking Rates (%)") %>% 
  gt_sparkline(Trend, 
               range_colors = c("#2E5A87", "#A90C38"),
               line_color = "gray", 
               width = 15) %>% 
  cols_align(columns = c("Women", "Men", "Total"), align = "center") %>% 
  gt_theme_538()


```




# Day 25: Trend (Uncertainties)

```{r d25-setup, include = FALSE}
p_load(climate)

temperature <- meteo_imgw(interval = "monthly", year = 1966:2020, station =  "ÅEBA")


```

```{r d25-plot, include = TRUE}
temperature %>% 
  group_by(yy, mm)
  mutate(date = paste0(yy, mm)) %>% 
  ggplot(aes(date, tmax_mean)) + 
  geom_point()
```

# Extra Stuff

```{r end-knit, include = FALSE}
knitr::knit_exit()
```
template, {rprojroot}, {rgbif}, {geoviz}, {ggmap}, {rayvista}, {camcorder}, {rayvertex}, {pwr}, {reprex}, debug = T for geom_text, {lcmm}, {rolldown}, {muvr}, {pcalg}, {packagemetrics}, {steveproj}, {ungeviz}, {themis}, {prettydoc}, {annotate}, {printy}, {roughsf}, {colorspace}, {monochromeR}, {colorblindr}, {echarts4r}, {ggtext}


<https://albert-rapp.de/post/2021-09-16-similar-data-and-list-like-columns/#helpful-concepts>

<https://www.swisstopo.admin.ch/>

<https://www.ign.es/web/ign/portal/cbg-area-cartografia>

<http://shadedrelief.com/SampleElevationModels/>

<https://www.neonscience.org/resources/learning-hub/tutorials>

<https://docs.ropensci.org/rgbif/articles/rgbif.html>

<https://ryo-n7.github.io/2020-05-14-webscrape-soccer-data-with-R/>

<https://github.com/gkaramanis/aRt/blob/master/split-bar/split-bar.R>

<https://github.com/thebioengineer/camcorder>

<https://gist.github.com/Worville/c4149ece45a75928a404d316151ba0fe>

<https://www.tjmahr.com/lists-knitr-secret-weapon/>