---
title: "Daily R - August 2021"
output: html_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  fig.retina = 3,
  fig.path = here::here("exports", "August", "/")
)

pacman::p_load(pacman, tidyverse, janitor, here, rio, job, skimr)

theme_set(theme_bw(base_size = 15))
```

# 20210802 - '{ggradar}'

```{r, include = F}
#devtools::install_github("ricardo-bion/ggradar", dependencies = TRUE)

p_load(ggradar, scales)

mtcars_radar <- mtcars %>% 
  as_tibble(rownames = "group") %>% 
  mutate_at(vars(-group), rescale) %>% 
  tail(3) %>% 
  select(1:10)

```

```{r}
ggradar(mtcars_radar, 
        group.colours = c("blue", "red", "green"), 
        values.radar = c("0", "0.5", "1.0"), 
        background.circle.colour = "white", 
        group.point.size = 1)
```

# 20210803 - #TidyTuesday and Paralympic Games

```{r, include = F}
p_load(tidytuesdayR)

tt <- tt_load("2021-08-03")
#readme(tt)

para <- tt$athletes

skim(para)

glimpse(para)

para %>% count(gender)

```

```{r, include = F}
repeat_winners <- para %>% 
  count(athlete) %>% 
  filter(n > 1) %>% 
  arrange(-n) %>% 
  filter(!is.na(athlete))

repeat_winners %>% 
  ggplot(aes(n)) + 
  geom_density()

most_medals <- repeat_winners %>% 
  head(10) %>% 
  filter(athlete != "-")

best_para <- para %>% 
  filter(athlete %in% most_medals$athlete) %>% 
  mutate(medal = factor(medal, levels = c("Bronze", "Silver", "Gold")))

```

```{r}
best_para %>% 
  ggplot(aes(athlete, fill = medal)) + 
  geom_bar() + 
  coord_flip() + 
  scale_fill_manual(values = c("#cd7f32", "#c0c0c0", "#ffd700")) + 
  labs(x = NULL, y = "Medal Count", title = "Most Decorated Paralympians and How Many of Each Medal They Won") + 
  theme_light() + 
  theme(plot.title.position = "plot", legend.title = element_blank(), 
        legend.position = c(0.8, 0.2), legend.background = element_blank())
```

# 20210804 - More #TidyTuesday and The Paralympics

```{r}
best_para %>% 
  ggplot(aes(athlete, fill = type)) + 
  geom_bar() + 
  coord_flip() + 
  scale_fill_manual(values = c("#bc4b4b", "#abcdef", "#9cd6a3", "#4e6b51")) + 
  labs(x = NULL, y = "Medal Count", title = "Most Decorated Paralympians and The Types of Sports They Play") + 
  theme_light() + 
  theme(plot.title.position = "plot", legend.title = element_blank(), 
        legend.position = c(0.8, 0.2), legend.background = element_blank())
```

# 20210805 - Trying {ggstatsplot}

Using {ggstatsplot} and {palmerpenguins} cause R to crash. Not sure why.

```{r, include = F}
p_load(ggstatsplot, palmerpenguins)

penguins

ggbetweenstats(iris, Species, Sepal.Length)

ggplot(penguins, aes(species, bill_length_mm)) + 
  geom_boxplot()

#ggbetweenstats(penguins, species, Sepal.Length)


```

```{r}
ggbetweenstats(
  data = penguins,
  x = species,
  y = bill_depth_mm,
  plot.type = "box"
)
```

# 20210806 - Trying {ggstatsplot} again

Had to update {Rcpp} and it works now.

```{r, include = F}
p_load(ggstatsplot)

ggstatsplot::bugs_wide

bugs <- bugs_wide

```


```{r}
bugs %>% 
  ggplot(aes(education, ldlf)) + 
  geom_boxplot() + 
  facet_wrap(~gender) + 
  coord_flip()

bugs %>% 
  ggplot(aes(education, ldhf)) + 
  geom_boxplot() + 
  facet_wrap(~gender) + 
  coord_flip()

bugs %>% 
  ggplot(aes(education, hdlf)) + 
  geom_boxplot() + 
  facet_wrap(~gender) + 
  coord_flip()

bugs %>% 
  ggplot(aes(education, hdhf)) + 
  geom_boxplot() + 
  facet_wrap(~gender) + 
  coord_flip()
```

```{r}
ggbetweenstats(bugs, education, ldlf)
```



# 20210809 - Working on a map of my parent's trip to Portland, OR

```{r}
stops <- import("or_trip.xlsx")

test <- map_data("state")

# ggplot(test, aes(long, lat)) + 
#   geom_sf(aes(group = group), fill = "white", color = "black") +
#   geom_point(data = stops, aes(x = lat, y = lon)) + 
#   theme_void()


```

# 20210810 - #TidyTuesday and U.S. Investment

```{r, include = F}
p_load(tidytuesdayR)

tt <- tt_load("2021-08-10")

readme(tt)


tt1 <- tt$investment

skim(tt1)

str(tt1)

tt1 %>% 
  count(meta_cat) %>% 
  View()


total_inv <- tt1 %>% 
  filter(str_detect(meta_cat, "^Total"))
```

```{r}
total_inv %>% 
  ggplot(aes(year, gross_inv, color = category)) +
  geom_point(size = 0.5) + 
  facet_wrap(~meta_cat) + 
  theme(legend.position = "bottom", legend.direction = "horizontal", legend.title = element_blank())
```

# 20210811 - More #TidyTuesday and Investment

```{r}
total_inv %>% 
  ggplot(aes(year, gross_inv, color = category)) +
  geom_line(size = 0.5) + 
  facet_wrap(~meta_cat) + 
  scale_y_continuous(labels=scales::dollar_format(), name = "") + 
  theme(legend.position = "bottom", legend.direction = "horizontal", legend.title = element_blank())
```

```{r, include = F}
other_inv <- tt1 %>% 
  filter(!str_detect(meta_cat, "^Total"))

other_inv %>% 
  count(category)
```

# 20210812 - Portland trip map

```{r, include = F}
p_load(rnaturalearth, rnaturalearthdata, sf, maps)

world <- ne_countries(scale = "medium", returnclass = "sf")

usa <- subset(world, admin %in% c("United States of America", "Canada", "Mexico"))
(mainland <- ggplot(data = usa) +
     geom_sf(fill = "white", color = "black") +
     coord_sf(crs = st_crs(2163), xlim = c(-2500000, 2500000), ylim = c(-2300000, 
         730000)))

states <- st_as_sf(map("state", plot = FALSE, fill = TRUE))
#states <- cbind(states, st_coordinates(st_centroid(states)))

ggplot(usa) + 
  geom_sf(fill = "white", color = "black", size = 0.05) +
#  coord_sf(crs = st_crs(2163), xlim = c(-2500000, 2500000), ylim = c(-2300000, 730000)) + 
  geom_point(data = stops, aes(x = lon, y = lat), size = 2) + 
  scale_x_continuous(limits = c(-125, -90)) + 
  scale_y_continuous(limits = c(32, 50)) + 
  geom_sf(data = states, fill = NA, size = 0.25) + 
  geom_segment(data = stops, aes(x = lon, y = lat, 
                    xend=c(tail(lon, n=-1), NA), 
                    yend=c(tail(lat, n=-1), NA)
                  ), lty = 2) +
  coord_sf() + 
  theme_void()



#browseURL("https://r-spatial.org/r/2018/10/25/ggplot2-sf-2.html")


```

# 20210813 - Portland again

```{r}
p_load(ggrepel)


(trip_map <- ggplot(usa) + 
  geom_sf(fill = "beige", color = "black", size = 0.05) +
  geom_point(data = stops, aes(x = lon, y = lat), size = 2) + 
  scale_x_continuous(limits = c(-125, -90)) + 
  scale_y_continuous(limits = c(32, 50)) + 
  geom_sf(data = states, fill = NA, size = 0.25) + 
  geom_segment(data = stops, aes(x = lon, y = lat, 
                    xend=c(tail(lon, n=-1), NA), 
                    yend=c(tail(lat, n=-1), NA)
                  ), lty = 2) +
  geom_label_repel(data = stops, aes(label = stop, x = lon, y = lat))+
  coord_sf() + 
  theme_void() + 
  theme(panel.background = element_rect(fill = "steelblue4"))
)
```


# 20210816 - OFF

# 20210817 - #TidyTuesday and Star Trek Voice Commands and {ggwaffle}

```{r, include = F}
p_load(tidytuesdayR, ggwaffle)

tt <- tt_load("2021-08-17")
readme(tt)

trek <- tt$computer %>% 
  mutate(type = str_to_title(type))

skim(trek)
```

```{r}
trek %>% 
  count(type) %>% 
  gt::gt()
```

```{r, include = F}
waffle_data <- waffle_iron(mpg, aes_d(group = class))

ggplot(waffle_data, aes(x, y, fill = group)) + 
  geom_waffle()

```



```{r}
trek_waffle <- waffle_iron(trek, aes_d(group = type), sample_size = 0.25, rows = 25)

ggplot(trek_waffle, aes(x = x, y = y, fill = group)) + 
  geom_waffle() + 
  coord_equal() + 
 # scale_fill_waffle() + 
  theme(legend.position = "bottom", legend.title = element_blank(), legend.direction = "horizontal") +
  theme_waffle() +
  labs(x = NULL, y = NULL)

```

# 20210818 - ISRHML
# 20210819 - ISRHML
# 20210820 - ISRHML

# 20210824 - Portland, Again

```{r}
trip_legend <- stops %>% 
  mutate(legend = 1) %>% 
  head(-1) %>% 
  ggplot(aes(legend, reorder(name, -stop))) + 
  geom_text(aes(label = paste0(stop, ":"))) +
  labs(x = NULL, y = NULL) +
  scale_y_discrete(position = "right") +
  scale_x_discrete(labels = NULL) + 
  theme_classic(base_size = 15, base_line_size = 0) +
  theme(axis.text = element_text(color = "black"))

trip_legend
```

# 20210824 - #TidyTuesdayR and Lemurs

```{r, include = F}
p_load(tidytuesdayR, ggbeeswarm)

#tt <- tt_load("2021-08-24")

#lemurs <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-08-24/lemur_data.csv')

lemurs <- import(here("data", "lemur_data.csv"))

skim(lemurs)
```

```{r}
lemurs %>% 
  filter(birth_type != "Unk") %>% 
  mutate(taxon = fct_reorder(taxon, age_at_death_y, .fun = "mean", na.rm = T)) %>% 
  ggplot(aes(taxon, age_at_death_y, fill = birth_type)) +
  geom_boxplot() + 
  coord_flip()
```

# 20210825 - Nothing
# 20210826 - portland

```{r}
p_load(patchwork, elevatr, sf, raster)

trip_map + trip_legend + plot_layout(widths = c(10, 0.5), heights = 10)


trip_map2 <- ggplot(usa) + 
  geom_sf(fill = "beige", color = "black", size = 0.05) +
  geom_point(data = stops, aes(x = lon, y = lat), size = 2) + 
  scale_x_continuous(limits = c(-125, -90)) + 
  scale_y_continuous(limits = c(32, 50)) + 
  geom_sf(data = states, fill = NA, size = 0.25) + 
  geom_segment(data = stops, aes(x = lon, y = lat, 
                    xend=c(tail(lon, n=-1), NA), 
                    yend=c(tail(lat, n=-1), NA)
                  ), lty = 2) +
  geom_label_repel(data = stops, aes(label = stop, x = lon, y = lat))+
  coord_sf() + 
  theme_void() + 
  theme(panel.background = element_rect(fill = "steelblue4"))


#browseURL("https://stackoverflow.com/questions/57024684/ggplot2-numbered-points-on-plot-and-in-legend")

```

```{r, include = F, eval = F}

#st_bbox(usa)

crop_usa <- st_crop(usa, ymin = 32, ymax = 50, 
                xmin = -125, xmax = -90)

ggplot(crop_usa) + 
  geom_sf(fill = "white", color = "black", size = 0.05)

elevation1 <- get_elev_raster(test, z = 8)

plot(elevation1)

crs(elevation1)

elevation <- raster::crop(elevation1, extent(crop_usa))

plot(elevation)

test3 <- st_crop(test2, ymin = 32, ymax = 50, 
                 xmin = -125, xmax = -90)

```

# 20210830 - Nothing. Home with kid.
# 20210831 - #TidyTuesdayR and Bird Baths in Australia and {treemap}

```{r, include = F}
p_load(tidytuesdayR, treemap)

tt <- tt_load("2021-08-31")
readme(tt)

birds <- tt$bird_baths

skim(birds)
```

```{r, include = F, eval = F}
birds %>% 
  group_by(survey_year, bird_type, bioregions) %>% 
  mutate(total = sum(bird_count)) %>% 
  filter(!is.na(bioregions)) %>% 
  ggplot(aes(bioregions, total, color = survey_year)) + 
  geom_point() +
  coord_flip() +
  facet_wrap(~bird_type)
```

```{r, include = F}
tot_birds <- birds %>% 
  dplyr::filter(bird_count > 1) %>% 
  mutate(bird_count2 = scale(bird_count)) %>% 
  arrange(-bird_count)

```


```{r}
tot_birds %>% 
  head(15) %>% 
  treemap(.,
          index = "bird_type",
          vSize = "bird_count",
          type = "index")
```


# Ideas

template, gtsummary, officedown/officer, glue/,gluedown tidymodels, ggsankey, groundhog, ezknitr, rprojroot, colorspace, rgbif, polite (web scraping), geoviz, magick, ggmap, ggstream, rayvista, circlize, camcorder, {renv}, {rayvertex}, {labelled}, {report}, {insight}, {performance}, {parameters}, {correlation}, {easystats}, {hrbrthemes}, {firatheme}, {pwr}, voronoi, {reprex}, {ggdag}, {dotwhisker}, {infer}, {aRtsy} 

<https://www.swisstopo.admin.ch/>

<https://www.ign.es/web/ign/portal/cbg-area-cartografia>

<http://shadedrelief.com/SampleElevationModels/>

<https://www.neonscience.org/resources/learning-hub/tutorials>

<https://docs.ropensci.org/rgbif/articles/rgbif.html>

<https://ryo-n7.github.io/2020-05-14-webscrape-soccer-data-with-R/>

<https://github.com/gkaramanis/aRt/blob/master/split-bar/split-bar.R>

<https://www.tidymodels.org/>

<https://rstudio.github.io/distill/basics.html>

<https://github.com/thebioengineer/camcorder>

<https://gist.github.com/Worville/c4149ece45a75928a404d316151ba0fe>