---
title: "Executable Manuscript || Quarto"
format:
  html:
    theme: simplex
    toc: true
    number-sections: true
  docx:
    toc: false
    section-numbers: true
    # output-file: here::here("ex_manuscript_files", "Test.docx")
---

## Creating an **"Executable Manuscript"** using Quarto

**Quarto** is the next generation of Rmarkdown and can be used to perform data analysis and word processing in the same document. It can export multiple formats including `html`, Word, and PowerPoint. It can also handle citations and automatically create a bibliography.

The goal for this document is to provide instructions for setting up and using **Quarto**.

### Quarto Setup

You have probably already completed some of these steps.

-   [Install R](https://cran.microsoft.com/)

-   [Install RStudio](https://www.rstudio.com/products/rstudio/download/)

-   Install `{quarto}` using `install.packages("quarto")`.

-   Other packages you might find useful:

    -   `{rio}` - import/export

    -   `{here}` - locating files/exports

    -   `{janitor}` - mainly just for the `clean_names()` function.

    -   `{pacman}` - can be used to import/install multiple packages at once.

### Packages and R Setup

```{r r-setup}
#| echo: true
#| warning: false

# install.packages("pacman")  # uncomment if you need to install {pacman}

pacman::p_load(rio, here, janitor, tidyverse)

pacman::p_load(palmerpenguins)  # example data set

palmerpenguins::penguins
```

```{r}

```
