---
title: "February 2022"
description: |
  DailyR practice file created using the Distill format.
author:
  - name: Clark Sims 
date: "`r Sys.Date()`"
output: distill::distill_article
knit: crsp::knit_to_outputs_folder

---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  fig.retina = 3,
  fig.path = here::here("exports", "February_2022", "/")
)

# knitr::opts_knit$set(
# #  root.dir = here::here(),
#   output.dir = here::here("html files")
# )

pacman::p_load(janitor, pacman, rio, skimr, here, conflicted,
               tidyverse, crsp)

conflict_prefer("clean_names", "janitor")
conflict_prefer("filter", "dplyr")

theme_set(theme_bw(base_size = 15) + theme(legend.position = "bottom"))

```

# 20220201: #TidyTuesday and Dog Breeds

```{r tt-import-feb-1, include = FALSE}
p_load(tidytuesdayR)
# 
# tt_raw <- tt_load("2022-02-01")
# 
# breed_rank_all <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2022/2022-02-01/breed_rank.csv')


breeds <- import(here("data", "tt", "breed_rank.csv")) %>% 
  pivot_longer(cols = 2:9, values_to = "rank") %>% 
  separate(name, into = c("year", "trash"), sep = " ") %>% 
  select(-trash) %>% 
  clean_names()

t10_breeds <- breeds %>% 
  group_by(breed) %>% 
  summarize(mean_ranking = mean(rank)) %>% 
  arrange(mean_ranking) %>% 
  head(10) %>% 
  pluck("breed")
```


```{r tt-plot-feb-1, include = FALSE}
breeds %>% 
  filter(breed %in% t10_breeds) %>% 
  ggplot(aes(year, rank, color = breed)) + 
  geom_point(size = 4, shape = 18) +
  geom_line(aes(group = breed), size = 2) + 
  geom_label(aes(label = breed), 
             data = breeds %>% filter(year == 2020, breed %in% t10_breeds), 
             nudge_x = 0.1, hjust = 0) +
  scale_y_reverse(breaks = c(2, 4, 6, 8, 10)) +
  labs(x = NULL, y = "Ranking") + 
  expand_limits(x = c(1, 11)) +
  paletteer::scale_color_paletteer_d("RColorBrewer::Set3") + 
  theme(legend.position = "none", 
        panel.border = element_blank(),
        panel.background = element_rect("white"),
        panel.grid.major.x = element_blank(),
        panel.grid.major.y = element_line(color = "black"),
        panel.grid.minor.y = element_line(color = "black"))

```


# 20220202: Custom `ggplot` Theme

Just for fun, I'm going to setup a custom plotting theme for ggplot. I may
incorporate this into `crsp` if it seems useful.

```{r crsp-theme, include = FALSE}

hexes <- c("#E1CE7A", "#006E90", "#C7CEDB", "#D36135", "#020202", "#FFFFFF")

scales::show_col(hexes)

theme_crsp <- function(..., base_size = 14) {
  theme(
    panel.grid.minor = element_blank()
  )
}

mtcars %>% 
  ggplot(aes(hp, mpg)) + 
  geom_point() + 
  geom_smooth(method = "lm", se = FALSE) + 
  theme_crsp()

```


# Ideas


{template}, {rprojroot}, {rgbif}, {geoviz}, {ggmap}, {rayvista}, {camcorder}, {renv}, {rayvertex}, {hrbrthemes}, {firatheme}, {pwr}, voronoi, {reprex}, debug = T for geom_text, {lcmm}, {rolldown}, {muvr}, {pcalg}, {packagemetrics}, {steveproj}, {ungeviz}, {themis}, {biscale}, {prettydoc}, {annotate}, {printy}, {roughsf}, {colorspace}

<https://github.com/richardvogg/30DayMapChallenge21>

<https://albert-rapp.de/post/2021-09-16-similar-data-and-list-like-columns/#helpful-concepts>

<https://www.swisstopo.admin.ch/>

<https://www.ign.es/web/ign/portal/cbg-area-cartografia>

<http://shadedrelief.com/SampleElevationModels/>

<https://www.neonscience.org/resources/learning-hub/tutorials>

<https://docs.ropensci.org/rgbif/articles/rgbif.html>

<https://ryo-n7.github.io/2020-05-14-webscrape-soccer-data-with-R/>

<https://github.com/gkaramanis/aRt/blob/master/split-bar/split-bar.R>

<https://github.com/thebioengineer/camcorder>

<https://gist.github.com/Worville/c4149ece45a75928a404d316151ba0fe>

<https://www.tjmahr.com/lists-knitr-secret-weapon/>