---
title: "February 2022"
description: |
  DailyR practice file created using the Distill format.
author:
  - name: Clark Sims 
date: "`r Sys.Date()`"
output: distill::distill_article
knit: crsp::knit_to_outputs_folder

---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  fig.retina = 3,
  fig.path = here::here("exports", "February_2022", "/")
)

# knitr::opts_knit$set(
# #  root.dir = here::here(),
#   output.dir = here::here("html files")
# )

pacman::p_load(janitor, pacman, rio, skimr, here, conflicted,
               tidyverse, crsp, gt)

conflict_prefer("clean_names", "janitor")
conflict_prefer("filter", "dplyr")

theme_set(theme_bw(base_size = 15) + theme(legend.position = "bottom"))

```

# 20220201: #TidyTuesday and Dog Breeds

```{r tt-import-feb-1, include = FALSE}
p_load(tidytuesdayR)
# 
# tt_raw <- tt_load("2022-02-01")
# 
# breed_rank_all <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2022/2022-02-01/breed_rank.csv')


breeds <- import(here("data", "tt", "breed_rank.csv")) %>% 
  pivot_longer(cols = 2:9, values_to = "rank") %>% 
  separate(name, into = c("year", "trash"), sep = " ") %>% 
  select(-trash) %>% 
  clean_names()

t10_breeds <- breeds %>% 
  group_by(breed) %>% 
  summarize(mean_ranking = mean(rank)) %>% 
  arrange(mean_ranking) %>% 
  head(10) %>% 
  pluck("breed")
```


```{r tt-plot-feb-1, include = FALSE}
breeds %>% 
  filter(breed %in% t10_breeds) %>% 
  ggplot(aes(year, rank, color = breed)) + 
  geom_point(size = 4, shape = 18) +
  geom_line(aes(group = breed), size = 2) + 
  geom_label(aes(label = breed), 
             data = breeds %>% filter(year == 2020, breed %in% t10_breeds), 
             nudge_x = 0.1, hjust = 0) +
  scale_y_reverse(breaks = c(2, 4, 6, 8, 10)) +
  labs(x = NULL, y = "Ranking") + 
  expand_limits(x = c(1, 11)) +
  paletteer::scale_color_paletteer_d("RColorBrewer::Set3", direction = -1) + 
  theme(legend.position = "none", 
        panel.border = element_blank(),
        panel.background = element_rect("#CCFFFF"),
        panel.grid.major.x = element_blank(),
        panel.grid.major.y = element_line(color = "black"),
        panel.grid.minor.y = element_line(color = "black"))

```


# 20220202 - 20220203: Custom `ggplot` Theme

Just for fun, I'm going to setup a custom plotting theme for ggplot. I may
incorporate this into `crsp` if it seems useful.

```{r crsp-theme, include = FALSE}
hexes <- c("#E1CE7A", "#006E90", "#C7CEDB", "#D36135", "#020202", "#FFFFFF")

scales::show_col(hexes)

theme_crsp <- function(..., base_size = 14) {
  theme(
      # plotting components
      
      ## drop minor gridlines
      panel.grid.minor = element_blank(),
      # change grid lines to gray
      panel.grid.major =  element_line(color = "#d0d0d0"),
      # fill the plot and panel spaces with grey and remove border
      panel.background = element_rect(fill = "white", color = NA),
      plot.background = element_rect(fill = "white", color = NA),
      panel.border = element_rect(color = "#d0d0d0"),
      # remove strip background
      strip.background = element_blank(),
      # adjust the margins of plots and remove axis ticks
#      plot.margin = margin(0.5, 1, 0.5, 1, unit = "cm"),
      axis.ticks = element_blank(),
      # change text family, size, and adjust position of titles
      text = element_text(family = "Chivo", size = base_size),
      axis.text = element_text(face = "bold", color = "black", size = base_size),
      axis.title = element_text(face = "bold", size = rel(1.33)),
      # axis.title.x = element_text(margin = margin(0.5, 0, 0, 0, unit = "cm")),
      # axis.title.y = element_text(margin = margin(0, 0.5, 0, 0, unit = "cm"), angle =90),
      plot.title = element_text(face = "bold", size = rel(1.67), hjust = 0),
      plot.title.position = "plot",
      # plot.subtitle = element_text(size = 16, margin = margin(0.2, 0, 1, 0, unit = "cm"), hjust = 0),
      # plot.caption = element_text(size = 10, margin = margin(1, 0, 0, 0, unit = "cm"), hjust = 1),
      strip.text = element_text(size = rel(1.33), face = "bold"),
      ...
    )
}
```


```{r crsp-theme-2, include = TRUE, echo = TRUE}
mtcars %>% 
  ggplot(aes(hp, mpg, fill = as.factor(cyl))) + 
  geom_smooth(method = "lm", se = FALSE, color = "black") + 
  geom_point(shape = 21, size = 4) + 
  scale_fill_manual(values = hexes) +
  labs(title = "No Theme", subtitle = "test 2", x = "Horse Power", y = "MPG", fill = "Cylinders")

mtcars %>% 
  ggplot(aes(hp, mpg, fill = as.factor(cyl))) + 
  geom_smooth(method = "lm", se = FALSE, color = "black") + 
  geom_point(shape = 21, size = 4) + 
  scale_fill_manual(values = hexes) +
  labs(title = "theme_crsp", subtitle = "test 2", x = "Horse Power", y = "MPG", fill = "Cylinders") +
  theme_crsp()

```

# 20220204: **[`{reactable}`](https://glin.github.io/reactable/index.html)** and Harry Potter Kaggle Dataset

```{r 04-setup, include = FALSE}
pacman::p_load(reactable)

hp <- import(here("data", "kaggle", "hp", "Characters.csv")) %>% 
  mutate(across(everything(), .fns = str_remove_all, "Â")) %>% 
  clean_names()
```

```{r 04-table, include = TRUE}
hp %>% 
  filter(blood_status == "Pure-blood") %>% 
  select(-id) %>% 
  rename_with(str_to_title, everything()) %>% 
  reactable()
```

# 20220207: **[`{reactable}`](https://glin.github.io/reactable/index.html)** and Harry Potter Kaggle Dataset - Number 2

```{r 05-setup, include = FALSE}
pacman::p_load(reactable)

hp <- import(here("data", "kaggle", "hp", "Characters.csv")) %>% 
  mutate(across(everything(), .fns = str_remove_all, "Â|â|€|™|˜")) %>% 
  clean_names() %>% 
  mutate_all(na_if, "") %>% 
  select(-c(id, wand, patronus, hair_colour, eye_colour))
```

```{r 05-table, include = TRUE}
hp %>% 
  filter(blood_status == "Pure-blood") %>% 
  rename_with(str_to_title, everything()) %>% 
  reactable(resizable = TRUE, 
            filterable = TRUE,
            searchable = TRUE, 
            showPageSizeOptions = TRUE, 
            highlight = TRUE)
```

Also see, **[`reactablefmtr`](https://github.com/kcuilla/reactablefmtr)**

# 20220208 and 20220209: #TidyTuesday and the Tuskegee Airmen

```{r tt-import-feb-8, include = FALSE}
p_load(tidytuesdayR, sf, maps)


tam_raw <- tt_load("2022-02-08")
readme(tam_raw)

tam <- tam_raw$airmen %>% 
  mutate(state = case_when(state == "HT" ~ "Haiti",
                           state == "CN" ~ "Canada",
                           state == "TD" ~ "Trinidad",
                           state == "In" ~ "IN",
                           state == "KN" ~ "KY",
                           state == "VI" ~ "U.S. Virgin Islands",
                           TRUE ~ state))

# skim(tam)
# 
# tam %>% count(state) %>% view()

states <- list(state.abb, state.name, state.center, state.region) %>% 
  reduce(bind_cols) %>% 
  rename("state" = 1, 
         "name" = 2, 
         "region" = 5) %>% 
  add_row(state = "DC",
          name = "District of Columbia",
          x = -77.03529789,
          y = 38.8961735,
          region = "South") %>% 
  mutate(.state = tolower(name))


# 38.89617352335707, -77.03529789133555


state_count <- tam %>% 
#  filter(!state %in% c("Haiti", "TD", "Unk", "CN"), !is.na(state)) %>%  # 3 from Haiti, 1 from Trinidad, 1 from Canada
  group_by(state) %>% 
  count() %>% 
  arrange(-n) %>% 
  left_join(states) %>% 
  mutate(qt_count = case_when(n < 25 ~ "< 25",
                              n >= 25 & n < 50 ~ "25 - 49",
                              n >= 50 & n < 75 ~ "50 - 74",
                              TRUE ~ ">= 75"))

us_map <- st_as_sf(maps::map("state", plot = FALSE, fill = TRUE)) %>% 
  rename(.state = ID) %>% 
  left_join(state_count) %>% 
  mutate(qt_count = case_when(is.na(qt_count) ~ "0",
                              TRUE ~ qt_count)) %>% 
  mutate(qt_count = factor(qt_count, levels = c("0", "< 25", "25 - 49", "50 - 74", ">= 75")))
```

```{r tam-map, include = FALSE}

tam_pal <- c("#211A1D" ,"#0608B2", "#FFF94F", "#FB3640", "#E6EED6")

scales::show_col(tam_pal)

us_map %>% 
  ggplot() +
  geom_sf(aes(fill = qt_count), color = "black") + 
  scale_fill_manual(values = rev(tam_pal), na.value = tam_pal[5]) +
#  guides(fill = guide_colorbar(barwidth = 20, barheight = 1, title.position = "top")) +
  labs(fill = "Number of Pilots") + 
  theme_void() +
  theme(legend.position = "bottom", legend.direction = "horizontal") +
  labs(title = "Where were the Tuskegee Airmen From?")
  

```

# 20220210 and 20220211: **[`ggvoronoi`](https://cran.r-project.org/web/packages/ggvoronoi/vignettes/ggvoronoi.html)**

```{r ggvoronoi-setup, include = FALSE}
p_load(ggvoronoi)

set.seed(45056)
x <- sample(1:200,100)
y <- sample(1:200,100)
points <- data.frame(x, y,
                     distance = sqrt((x - 100)^2 + (y - 100)^2))

circle <- data.frame(x = 100*(1 + cos(seq(0, 2*pi, length.out = 2500))),
                     y = 100*(1 + sin(seq(0, 2*pi, length.out = 2500))),
                     group = rep(1,2500))


set.seed(20220211)
x2 <- sample(1:200,100)
y2 <- sample(1:200,100)
points2 <- data.frame(x2, y2,
                     distance = sqrt((x2 - 100)^2 + (y2 - 100)^2))

```



```{r ggvoronoi-plots, include = TRUE}
ggplot(data = points, aes(x = x, y = y, fill = distance)) + 
  geom_voronoi(outline = circle, color = "white", show.legend = FALSE) +
  paletteer::scale_fill_paletteer_c("ggthemes::Orange-Blue-White Diverging") + 
  coord_fixed(ratio = 1) + 
  theme(legend.position = "none") +
  theme_void()

ggplot(data = points2, aes(x = x2, y = y2, fill = distance)) + 
  geom_voronoi(outline = circle, color = "white", show.legend = FALSE) +
  paletteer::scale_fill_paletteer_c("ggthemes::Red-Green-White Diverging") + 
  coord_fixed(ratio = 1) + 
  theme(legend.position = "none") +
  theme_void()
```



# 20220214: **[`ggvoronoi`](https://cran.r-project.org/web/packages/ggvoronoi/vignettes/ggvoronoi.html)** in a heart

```{r heart-setup, include = FALSE}
p_load(ggvoronoi)

set.seed(0214)
x3 <- sample(0:30, 25)
y3 <- sample(0:30, 25)
points3 <- data.frame(x, y,
                      distance = sqrt((x - 15)^2 + (y - 15)^2))

xhrt <-  function(t) 16*sin(t)^3
yhrt  <-  function(t) 13*cos(t) - 5*cos(2*t) - 2*cos(3*t) - cos(4*t)

heart <- data.frame(t = seq(0, 2*pi, by = 0.01)) %>% 
  mutate(x = xhrt(t) + 15,
         y = yhrt(t) + 15, 
         group = 1) %>% 
  select(-t)

ggplot(data = points, aes(x = x, y = y, fill = distance)) + 
  geom_voronoi(outline = heart, color = "white", show.legend = FALSE) +
  paletteer::scale_fill_paletteer_c("ggthemes::Classic Red") + 
  coord_fixed(ratio = 1) + 
  theme(legend.position = "none") +
  theme_void()

```

# 20220215 and 20220216: #TidyTuesday and #DuBoisChallenge2022

I'm going to try Day 6.

```{r tt-feb-wk-2, include = FALSE}
# p_load(tidytuesdayR)
# 
# tt_raw <- tt_load("2022-02-15")

d6 <- tibble::tribble(
  ~date, ~illiteracy,
  1860,              99,
  1870,            92.1,
  1880,            81.6,
  1890,            67.2,
  1900,              50
  )
```

```{r webd-d6, include = TRUE}
d6 %>% 
  ggplot(aes(illiteracy/100, date)) + 
  geom_point() + 
  geom_segment(aes(x = illiteracy/100, xend = illiteracy/100, y = date, yend = 1930), color = "black", size = 5) +
  geom_segment(aes(x = illiteracy/100, xend = 1, y = date, yend = date), color = "black", size = 5) +
  geom_segment(aes(x = illiteracy/100, xend = 1, y = date, yend = date), color = "antiquewhite1", size = 4) +
  scale_y_reverse(limits = c(1930, 1860)) +
# scale_x_continuous(labels = scales::percent)
  scale_x_reverse(labels = scales::percent) + 
#  coord_fixed(ratio = 1.2) +
  labs(y = NULL, x = "Percent Of Illiteracy") + 
  theme_classic() + 
  theme(axis.ticks = element_blank(), axis.line = element_blank(), 
        plot.background = element_rect("antiquewhite1"), panel.background = element_rect("antiquewhite1"),
        aspect.ratio = 1.2)
```
 
It'll do for the amount of time I have.

# 20220217: **[{engsoccerdata}](https://github.com/jalapic/engsoccerdata)**

```{r esd-setup, include = FALSE}
p_load(engsoccerdata, reactable)

data(package = "engsoccerdata")

str(mls)

```

```{r esd-tests, include = TRUE}
mls %>% 
  filter(round == "regular") %>% 
  maketable_all() %>% 
  rename("Team" = team, "Goals For" = gf, "Goals Allowed" = ga, "Goal Difference" = gd, "Overall Position" = Pos) %>% 
  reactable(resizable = TRUE, 
#            filterable = TRUE,
#            searchable = TRUE, 
            showPageSizeOptions = TRUE, 
            highlight = TRUE)
```

# Ideas


{template}, {rprojroot}, {rgbif}, {geoviz}, {ggmap}, {rayvista}, {camcorder}, {renv}, {rayvertex}, {hrbrthemes}, {firatheme}, {pwr}, voronoi, {reprex}, debug = T for geom_text, {lcmm}, {rolldown}, {muvr}, {pcalg}, {packagemetrics}, {steveproj}, {ungeviz}, {themis}, {biscale}, {prettydoc}, {annotate}, {printy}, {roughsf}, {colorspace}, {monochromeR}, {colorblindr}, {engsoccerdata} 


```{r end-knit, include = FALSE}
knitr::knit_exit()
```
<https://github.com/richardvogg/30DayMapChallenge21>

<https://albert-rapp.de/post/2021-09-16-similar-data-and-list-like-columns/#helpful-concepts>

<https://www.swisstopo.admin.ch/>

<https://www.ign.es/web/ign/portal/cbg-area-cartografia>

<http://shadedrelief.com/SampleElevationModels/>

<https://www.neonscience.org/resources/learning-hub/tutorials>

<https://docs.ropensci.org/rgbif/articles/rgbif.html>

<https://ryo-n7.github.io/2020-05-14-webscrape-soccer-data-with-R/>

<https://github.com/gkaramanis/aRt/blob/master/split-bar/split-bar.R>

<https://github.com/thebioengineer/camcorder>

<https://gist.github.com/Worville/c4149ece45a75928a404d316151ba0fe>

<https://www.tjmahr.com/lists-knitr-secret-weapon/>