---
title: "Daily R - February 2021"
output: html_document
---

# {.tabset .tabset-pills}

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)

pacman::p_load(pacman, tidyverse, rio, ggpubr, corrplot, janitor, broom, broom.mixed, lme4,
               ggdark,  # 
               RColorBrewer,  # 
               httr, XML,  # for Wikipedia scraping
               ggrepel,
               plotly,
               gt,  # tables
               ggdark,  # dark theme
               tidytuesdayR,
               rstatix,
               ggthemes,
               plotrix
)

theme_set(theme_bw())

```

## 20210209

Just trying a random included data set and seeing what happens.

```{r, echo = F, include = F}
df <- datasets::Harman23.cor$cov 

str(df)
head(df)
```


``` {r, out.width = '75%', echo = F}
corrplot(df, is.corr = T, type = "lower")

corrplot(df, is.corr = T, type = "lower", diag = F)

corrplot(df, is.corr = T, type = "lower", diag = F, method = "number")

corrplot(df, is.corr = T, type = "upper", diag = F, method = "ellipse", col = brewer.pal(n = 8, name = "Set1"))


```

## 20210210

Pulling MLS stadium locations from Wikipedia and mapping.

```{r, include = F}
#library(pacman) 

#p_load(tidyverse, rio, ggpubr, corrplot, RColorBrewer, janitor, broom, broom.mixed, lme4, ggdark)

### MLS

#p_load(httr, XML, sf, rnaturalearth, rnaturalearthdata, rgeos, maps, mapdata, ggmap, ggrepel, plotly)

# Get coordinates
url <- "https://en.wikipedia.org/wiki/List_of_Major_League_Soccer_stadiums"

r <- GET(url)

doc <- readHTMLTable(
  doc=content(r, "text"))

stadia <- doc[[2]] %>% 
  row_to_names(1) %>% 
  separate(Coordinates, sep = "/", into = c("A", "B", "C")) %>% 
  mutate(B = str_trim(B, "both")) %>% 
  separate(B, sep = " ", into = c("B2", "B3"), remove = F) %>% 
  mutate(lat = as.numeric(gsub("[^0-9.]", "", B2)),
         lon = -1*as.numeric(gsub("[^0-9.]", "", B3)))


us <- map_data("state")
```

```{r, out.width = '100%', echo = F}
(mls_map <- ggplot() + 
  geom_polygon(data = us, aes(x=long, y = lat, group = group), fill = NA, color = "gray") + 
  coord_fixed(1.3) + 
  geom_point(data = stadia, aes(x = lon, y = lat), color = "red", size = 3, shape = 1) + 
  geom_text_repel(data = stadia, aes(x = lon, y = lat, label = Franchise), min.segment.length = 0) + 
  theme_void()
)


mls_map2 <- ggplot() + 
  geom_polygon(data = us, aes(x=long, y = lat, group = group), fill = NA, color = "gray") + 
  coord_fixed(1.3) + 
  geom_point(data = stadia, aes(x = lon, y = lat), color = "red", size = 3, shape = 1) + 
  geom_text(data = stadia, aes(x = lon, y = lat, label = Franchise), check_overlap = T) + 
  theme_void()


ggplotly(mls_map2)
```

## 20210211


### Another MLS Plot
Adding stadium size and soccer specific detail
```{r, include = F, echo = F}
str(stadia)

stadia <- stadia %>% 
  separate(Capacity, into = c("MLS", "Other", sep = c("(", "["))) %>% 
  mutate(cap = as.numeric(paste0(MLS, Other))) %>% 
  mutate(cap = case_when(is.na(cap) ~ 69143, 
                         TRUE ~ cap)) %>% 
  select(2, 3, 4, 23, 5, 10, 11, 12, 18, 19, 21:22) %>% 
  rename(specific = "Soccer specific")
```

``` {r, out.width = '100%'}
(mls_map2 <- ggplot() + 
  geom_polygon(data = us, aes(x=long, y = lat, group = group), fill = NA, color = "gray") + 
  coord_fixed(1.3) + 
  geom_point(data = stadia, aes(x = lon, y = lat, size = cap, color = specific), shape = 1) + 
  geom_text_repel(data = stadia, aes(x = lon, y = lat, label = Franchise), min.segment.length = 0) + 
  theme_void() +
  theme(legend.position = "bottom") + 
  labs(size = "Capacity", color = "Soccer Specific?")
)

```

### Oranges Data Set

Looking at another data set
```{r, include = F, }
# data() # view all included datasets

orange <- Orange %>% 
  mutate(Tree = factor(Tree, levels = c("1", "2", "3", "4", "5")))

str(orange)

m1 <- lm(circumference ~ age, data = orange)
tidy(m1)

m2 <- lmer(circumference ~ age + (1|Tree), data = orange)

tidy(m2)
m2_ci <- confint(m2) %>% 
  as.data.frame() %>% 
  slice(c(3,4)) %>% 
  rownames_to_column("term")
```

```{r, fig.height = 6, fig.width = 8, fig.align = 'right'}
ggplot(orange, aes(age, circumference, color = Tree)) + 
  geom_point() + 
  geom_line() + 
  labs(x = "Age (Days)", y = "Circumference (mm)") + 
  scale_colour_brewer(palette = "Oranges") + 
  dark_theme_bw() + 
  theme(legend.position = "bottom")

```


## 20210212

Making some tables using m1 from yesterday.

```{r, include = F}
m2_gt <- m2 %>% 
  tidy() %>%
  filter(effect == "fixed") %>% 
  left_join(m2_ci) %>% 
  select(-effect, -group) %>% 
  clean_names("title") %>% 
  rename("Std. Error" = "Std Error",
         "2.5%" = "X2 5 Percent",
         "97.5%" = "X97 5 Percent")
```

### Basic Table of LM Example

```{r, echo = F}
m1 %>% 
  tidy() %>% 
  gt()
```

### Additional options on table for LMEM example.

```{r, echo = F}
m2_gt %>% 
  gt() %>% 
  tab_header(
    title = "Linear Mixed Effect Modeling of the Influence of Orange Tree Age on Tree Circumference"
  ) %>% 
  tab_spanner(label = "95% C.I.", columns = c(5,6))
```


## 20210215

President's Day

```{r}

```


## 20210216

Tidy Tuesday - February 16, 2021

W. E. B. DuBois Visualizations

```{r, include = F}
tt <- tt_load("2021-02-16")
readme(tt)


tt1 <- tt$georgia_pop


tt1 %>% ggplot(aes(Year, Colored)) + geom_line(color = "black") + 
  geom_line(aes(Year, White), lty = 2, color = "black") + 
  coord_flip() + 
  scale_y_reverse()


tt2 <- tt$conjugal %>% 
  pivot_longer(cols = 3:5, names_to = "Status") %>% 
  mutate(Population = factor(Population, levels = c("Germany", "Negroes")))
```


```{r}
ggplot(tt1, aes(y=White, x=Year))+
  geom_line(aes(colour="White",linetype= "White"))+
  geom_line(aes(y=Colored,x=Year, colour="Colored",linetype="Colored"))+
  coord_flip()+
  labs(title = "COMPARATIVE INCREASE OF WHITE AND COLORED \n POPULATION OF GEORGIA.")+
  scale_x_continuous(breaks = seq(1790, 1890, by = 10), name='', expand = c(0, 0))+
  scale_y_continuous(breaks = seq(0, 100, by = 5),name="Percents", trans="reverse", expand = c(0, 0))+
  scale_color_manual(values=c("black","black"))+
  scale_linetype_manual(values=c("Colored"=1,"White"=2))+
  guides(color = FALSE) + 
  theme(legend.position = "bottom", legend.title = element_blank())

```

```{r}
tt2 %>% ggplot(aes(reorder(Population, -value), value, fill = Status)) + 
  geom_col() + 
  coord_flip() +
  facet_wrap(~Age, nrow = 3, strip.position = "left") + 
  theme_minimal() +
  labs(x = "", y = "") + 
  theme(legend.position = "top", legend.title = element_blank()) +
  scale_fill_manual(values = c("Single" = "darkgreen",
                                "Married" ="darkgoldenrod1",
                                "Divorced and Widowed"="red4")) 


```

## 20210217

RM ANOVA on orange

It doesn't work for this data set because the measurements are not all at the same times. Just use the LMEM from above.

```{r}


ggqqplot(orange, "circumference", ggtheme = theme_bw()) +
  facet_wrap(~ Tree)


#anova_test(data = orange, dv = circumference, wid = Tree, within = age) %>% 
#  get_anova_table()
```

## 20210218

```{r, include = F}
df <- datasets::faithful

str(df)
```

```{r}
df %>% ggplot(aes(waiting, eruptions, color = eruptions > 3)) + 
  geom_jitter(shape = 1, show.legend = F) + 
  stat_ellipse(show.legend = F) + 
  labs(x = "Waiting Time (min)",
       y = "Eruption Duration (min)") + 
  scale_color_viridis_d() + 
  theme_tufte()
  


```


## 20210219

EMMs

```{r}
library(emmeans)

noise.lm <- lm(noise ~ size * type * side, data = auto.noise)
# Interaction plot of predictions
emmip(noise.lm, type ~ size | side)
# Confidence intervals
plot(emmeans(noise.lm, ~ size | side*type))

emmeans(noise.lm, specs = c("size", "side", "type"))

```

## 20210222

More EMMs

```{r}

test <- ref_grid(noise.lm)

test@grid
```

learnr?? writing functions?? datapasta?? augment?? tidymodels??
## 20210223

Tidy Tuesday - February 23, 2021

Employed Status

```{r, include = F}
tt <- tt_load("2021-02-23")
readme(tt)


tt1 <- tt$earn
tt2 <- tt$employed

```

```{r}
tt1 %>% ggplot(aes(median_weekly_earn, sex, fill = sex)) +
  geom_col() + 
  scale_fill_brewer(palette = "Accent") + 
  labs(y = "", x = "Median Weekly Earnings") + 
  scale_x_continuous(labels=scales::dollar_format()) + 
  facet_wrap(~ race) + 
  theme(legend.position = "none") + 
  theme_light()
```

```{r, include = F}
tt2 %>% ggplot(aes(industry, ""), stat = "prop") + 
  geom_col() + 
  coord_flip() + 
  facet_wrap(~ race_gender)

```

## 20210224

```{r, echo = F}
df <- tibble(x = seq(0, 10, by = 0.5),
             y = (1:21))

df %>% ggplot(aes(x, y)) + geom_point()


df2 <- tibble(x = c(1, 1, 2, 2),
              y = c(1, 2, 1, 2), 
              lab = c("A", "B", "C", "D"), 
              col = c("blue", "brown", "cyan", "darkgreen"))

df2 %>% ggplot(aes(x, y, color = col)) + geom_text(aes(label = lab), show.legend = F) + 
  scale_colour_identity()
```

``` {r, include = F, eval = F}

x = 16 * sin(t)^3
y = 13 * cos(t) - 5 * cos(2 * t) - 2 * cos(3 * t) - cos(4 * t)
t  <-  c(0:2 * pi)


df3 <- tibble(x = c(16 * sin(t)^3),
              y = c(13 * cos(t) - 5 * cos(2 * t) - 2 * cos(3 * t) - cos(4 * t)))

df3 %>% ggplot(aes(x, y)) + geom_point()

dat <- data.frame(t = seq(0, 2*pi, by = 0.01))
x <-  function(t) 16 * sin(t)^3
y <- function(t) 13*cos(t) - 5*cos(2*t) - 2*cos(3*t) - cos(4*t)

dat$y <- y(dat$t)
dat$x <- x(dat$t)

heart <- ggplot(dat, aes(x,y)) +
  geom_polygon(fill = "red", col = "firebrick", alpha = 0.9) +
  theme_classic()

heart

#plot.new()
#draw.circle(1, 1, pi,nv=100,border=NULL,col=NA,lty=1,density=NULL, angle=45,lwd=1)
```

## 20210225

```{r, echo = F}

df <- tibble(x = seq(1, 3, by = 0.025),
             y = rep_len(c(1, 1.5, 2, 2.5), 81))

df %>% ggplot(aes(x, y)) + geom_point() +
  ylim(c(0, 5)) + 
  xlim(c(0,5))

```



## 20210226

Trying the name aesthetic in ggplot

```{r, include = F}
employed <- tt2

employed_tidy <- employed %>%
  filter(!is.na(employ_n)) %>%
  group_by(occupation = paste(industry, minor_occupation), race_gender) %>%
  summarise(n = mean(employ_n)) %>%
  ungroup()

employment_demo <- employed_tidy %>%
  filter(race_gender %in% c("Women", "Black or African American", "Asian")) %>%
  pivot_wider(names_from = race_gender, values_from = n, values_fill = 0) %>%
  janitor::clean_names() %>%
  left_join(employed_tidy %>%
    filter(race_gender == "TOTAL") %>%
    select(-race_gender) %>%
    rename(total = n)) %>%
  filter(total > 1e3) %>%
  mutate(across(c(asian, black_or_african_american, women), ~ . / (total)),
    total = log(total),
    across(where(is.numeric), ~ as.numeric(scale(.)))
  ) %>%
  mutate(occupation = snakecase::to_snake_case(occupation))

employment_demo


employment_clust <- kmeans(select(employment_demo, -occupation), centers = 3)


```

```{r}
augment(employment_clust, employment_demo) %>%
  ggplot(aes(total, black_or_african_american, color = .cluster)) +
  geom_point()
```

```{r, include F}
kclusts <-
  tibble(k = 1:9) %>%
  mutate(
    kclust = map(k, ~ kmeans(select(employment_demo, -occupation), .x)),
    glanced = map(kclust, glance),
  )

kclusts %>%
  unnest(cols = c(glanced)) %>%
  ggplot(aes(k, tot.withinss)) +
  geom_line(alpha = 0.5, size = 1.2, color = "midnightblue") +
  geom_point(size = 2, color = "midnightblue")

final_clust <- kmeans(select(employment_demo, -occupation), centers = 5)
```

```{r}
p <- augment(final_clust, employment_demo) %>%
  ggplot(aes(total, women, color = .cluster, name = occupation)) +
  geom_point() +
  labs(x = "Total", y = "Women")

ggplotly(p, height = 500)
```

