---
title: "Daily R - July 2021"
output: html_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  fig.retina = 3,
  fig.path = here::here("exports", "July", "/")
)

pacman::p_load(pacman, tidyverse, janitor, here, rio, job, skimr)

theme_set(theme_bw(base_size = 15))
```

July wasn't my best month :). I will try again in August.

# 20210701 - Nothing
# 20210702 - Nothing
# 20210706 - #TidyTuesdayR and Independence Days.

```{r, tt-1}
p_load(tidytuesdayR, sf, rnaturalearth, rnaturalearthdata, rgeos)

#tt <- tt_load("2021", week = 28)$holidays
#tt <- import(here("data", "tt_wk28.xlsx"))

world <- ne_countries(scale = "medium", returnclass = "sf") %>% 
  left_join(tt %>% rename(name = country)) %>% 
  mutate(always_free = case_when(is.na(independence_from) ~ "No Independence Day",
                                 TRUE ~ "Has an Independence Day"))

ggplot(data = world) +
  geom_sf(aes(fill = year_of_event)) + 
  theme_void() + 
  theme(legend.position = "bottom", legend.direction = "horizontal")
```

# 20210707 - #TidyTuesdayR and Independance Days with {ggiraph}

```{r}
p_load(ggiraph)

ind_from <- ggplot(data = world) +
  geom_sf(aes(fill = independence_from)) + 
  theme_void() + 
  theme(legend.position = "bottom", legend.direction = "horizontal")

ind_when <- ggplot(data = world) +
  geom_sf(aes(fill = as.factor(year_of_event))) + 
  theme_void() + 
  theme(legend.position = "none", legend.direction = "horizontal")

ind_ever <- ggplot(data = world) +
  geom_sf_interactive(aes(fill = always_free, tooltip = independence_from)) + 
  scale_fill_manual(values = c("#F5C7CF", "#A4B4CC")) + 
  theme_void() + 
  theme(legend.position = "none", legend.direction = "horizontal")

girafe(ggobj = ind_ever)
```

```{r}
ind_ever_africa <- world %>% 
  filter(continent == "Africa") %>% 
  ggplot() +
  geom_sf_interactive(aes(fill = independence_from, tooltip = independence_from)) + 
#  scale_fill_manual(values = c("#F5C7CF", "#A4B4CC")) + 
  theme_void() + 
  theme(legend.position = "none", legend.direction = "horizontal")

girafe(ggobj = ind_ever_africa)
```


# 20210708 - Nothing
# 20210709 - Nothing
# 20210712 - Looked into {hrbrthemes}

They are some themes for {ggplot} that [@hrbrmstr](https://github.com/hrbrmstr) has made in a separate package.


# Ideas

template, gtsummary, officedown/officer, glue/,gluedown tidymodels, ggsankey, groundhog, ezknitr, rprojroot, colorspace, rgbif, polite (web scraping), geoviz, magick, ggmap, ggstream, rayvista, circlize, camcorder, {renv}, {rayvertex}, {labelled}, {ggradar}, {ggstatplots}, {report}, {insight}, {performance}, {parameters}, {correlation}, {easystats}, {hrbrthemes}, {firatheme}, {pwr}, voronoi

<https://www.swisstopo.admin.ch/>

<https://www.ign.es/web/ign/portal/cbg-area-cartografia>

<http://shadedrelief.com/SampleElevationModels/>

<https://www.neonscience.org/resources/learning-hub/tutorials>

<https://docs.ropensci.org/rgbif/articles/rgbif.html>

<https://ryo-n7.github.io/2020-05-14-webscrape-soccer-data-with-R/>

<https://github.com/gkaramanis/aRt/blob/master/split-bar/split-bar.R>

<https://www.tidymodels.org/>

<https://rstudio.github.io/distill/basics.html>

<https://github.com/thebioengineer/camcorder>

<https://gist.github.com/Worville/c4149ece45a75928a404d316151ba0fe>