---
title: "Daily R - March 2021"
output: html_document
---

# {.tabset .tabset-pills}

## Packages

```{r setup, include=FALSE, eval = T}
knitr::opts_chunk$set(echo = F)

pacman::p_load(pacman, tidyverse, rio, ggpubr, corrplot, janitor, broom, broom.mixed, lme4,
               ggdark,  # 
               RColorBrewer,  # 
               httr, XML,  # for Wikipedia scraping
               ggrepel,
               plotly,
               gt,  # tables
               ggdark,  # dark theme
               tidytuesdayR,
               rstatix,
               ggthemes,
               plotrix,
               rayshader,
               leaflet, 
               gghighlight, 
               ggbump, 
               ggtext, 
               scales, 
               gt,
               car
)

theme_set(theme_bw())


#usethis::create_github_token()
#usethis::edit_r_environ()
#gitcreds::gitcreds_set(url = "https://github.com")

#substr(gh::gh_token(), 1, 4)

```

```{r, eval = F}
library(tidyverse)
library(pacman)
library(rio)
library(tidytuesdayR)
library(gghighlight)
library(plotly)

theme_set(theme_bw())

```

## 20210301

rayshader

```{r, include = F}
p_load(rayshader, leaflet)

bbox <- list(
  p1 = list(long = -122.522, lat = 37.707),
  p2 = list(long = -122.354, lat = 37.84)
)

define_image_size <- function(bbox, major_dim = 400) {
  # calculate aspect ration (width/height) from lat/long bounding box
  aspect_ratio <- abs((bbox$p1$long - bbox$p2$long) / (bbox$p1$lat - bbox$p2$lat))
  # define dimensions
  img_width <- ifelse(aspect_ratio > 1, major_dim, major_dim*aspect_ratio) %>% round()
  img_height <- ifelse(aspect_ratio < 1, major_dim, major_dim/aspect_ratio) %>% round()
  size_str <- paste(img_width, img_height, sep = ",")
  list(height = img_height, width = img_width, size = size_str)
}

get_usgs_elevation_data <- function(bbox, size = "400,400", file = NULL, 
                                    sr_bbox = 4326, sr_image = 4326) {
  require(httr)
  
  # TODO - validate inputs
  
  url <- parse_url("https://elevation.nationalmap.gov/arcgis/rest/services/3DEPElevation/ImageServer/exportImage")
  res <- GET(
    url, 
    query = list(
      bbox = paste(bbox$p1$long, bbox$p1$lat, bbox$p2$long, bbox$p2$lat,
                   sep = ","),
      bboxSR = sr_bbox,
      imageSR = sr_image,
      size = size,
      format = "tiff",
      pixelType = "F32",
      noDataInterpretation = "esriNoDataMatchAny",
      interpolation = "+RSP_BilinearInterpolation",
      f = "json"
    )
  )
  
  if (status_code(res) == 200) {
    body <- content(res, type = "application/json")
    # TODO - check that bbox values are correct
    # message(jsonlite::toJSON(body, auto_unbox = TRUE, pretty = TRUE))
    
    img_res <- GET(body$href)
    img_bin <- content(img_res, "raw")
    if (is.null(file)) 
      file <- tempfile("elev_matrix", fileext = ".tif")
    writeBin(img_bin, file)
    message(paste("image saved to file:", file))
  } else {
    warning(res)
  }
  invisible(file)
}

image_size <- define_image_size(bbox, major_dim = 600)

```

```{r, eval = F}
montereybay %>%
  sphere_shade(zscale = 10, texture = "imhof1") %>%
  add_shadow(ray_shade(montereybay, zscale = 50)) %>%
  add_shadow(ambient_shade(montereybay, zscale = 50)) %>%
  plot_3d(montereybay, zscale = 50, theta = -45, phi = 45, water = TRUE,
          windowsize = c(1000,800), zoom = 0.75, waterlinealpha = 0.3,
          wateralpha = 0.5, watercolor = "lightblue", waterlinecolor = "white")
render_snapshot()
```

```{r}

water_palette = colorRampPalette(c("darkblue", "dodgerblue", "lightblue"))(300)
bathy_hs = height_shade(montereybay, texture = water_palette)

montereybay %>%
 sphere_shade(zscale=10, texture = "imhof2") %>%
 add_overlay(generate_altitude_overlay(bathy_hs, montereybay, 0, 0))  %>%
 add_shadow(ray_shade(montereybay,zscale=50),0.3) %>%
 plot_map()


#montereybay, zscale = 50, theta = -45, phi = 45, water = TRUE,
#          windowsize = c(1000,800), zoom = 0.75, waterlinealpha = 0.3,
#          wateralpha = 0.5, watercolor = "lightblue", waterlinecolor = "white"
```


```{r, eval = T, include = F}
bbox <- list(
  p1 = list(long = -122.522, lat = 37.707),
  p2 = list(long = -122.354, lat = 37.84)
)

leaflet() %>%
  addTiles() %>% 
  addRectangles(
    lng1 = bbox$p1$long, lat1 = bbox$p1$lat,
    lng2 = bbox$p2$long, lat2 = bbox$p2$lat,
    fillColor = "transparent"
  ) %>%
  fitBounds(
    lng1 = bbox$p1$long, lat1 = bbox$p1$lat,
    lng2 = bbox$p2$long, lat2 = bbox$p2$lat,
  )


#elev_file <- file.path(getwd(), "data", "sf-elevation.tif")
get_usgs_elevation_data(bbox, size = image_size$size, file = "sf.tif",
                        sr_bbox = 4326, sr_image = 4326)

elev_img <- raster::raster("sf.tif")
elev_matrix <- matrix(
  raster::extract(elev_img, raster::extent(elev_img), buffer = 1000), 
  nrow = ncol(elev_img), ncol = nrow(elev_img)
)

ambmat <- ambient_shade(elev_matrix, zscale = 30)
raymat <- ray_shade(elev_matrix, zscale = 30, lambert = TRUE)
watermap <- detect_water(elev_matrix)
```


```{r}
elev_matrix %>%
  sphere_shade(texture = "imhof4") %>%
  add_water(watermap, color = "imhof4") %>%
  add_shadow(raymat, max_darken = 0.5) %>%
  add_shadow(ambmat, max_darken = 0.5) %>%
  plot_map()
```

```{r, include = F, eval = F}
zscale <- 10
rgl::clear3d()
elev_matrix %>% 
  sphere_shade(texture = "imhof4") %>% 
  add_water(watermap, color = "imhof4") %>%
#  add_overlay(overlay_img, alphalayer = 0.5) %>%
  add_shadow(raymat, max_darken = 0.5) %>%
  add_shadow(ambmat, max_darken = 0.5) %>%
  plot_3d(elev_matrix, zscale = zscale, windowsize = c(1200, 1000),
          water = TRUE, soliddepth = -max(elev_matrix)/zscale, wateralpha = 0,
          theta = 25, phi = 30, zoom = 0.65, fov = 60)
render_snapshot()
```

## 20210302

Tidy Tuesday - Super Bowl Commercials

``````{r, include = F}

tt <- tt_load("2021-03-02")
readme(tt)

sb_com <- tt$youtube


sb_com2 <- sb_com %>% 
  filter(funny == F & show_product_quickly == F & patriotic == F & celebrity == F &
         danger == F & animals == F & use_sex == F)

sb_com2 %>% ggplot(aes(view_count, like_count)) + 
  geom_point() + 
  geom_text(aes(label = brand))
```

```{r, fig.width = 8, fig.height = 24, echo = F, message = F, warning = F}
sb_com %>% 
  count(brand, year) %>% 
  ggplot(aes(brand, n)) + 
  geom_col() + 
  labs(x = "", y = "Number of Commercials") + 
  coord_flip() + 
  facet_wrap(~ year, nrow = 7, ncol = 3)

```


## 20210303

more rayshader

```{r, include = F}
bbox2 <- list(
  p1 = list(long = -122.798248, lat = 37.566351),
  p2 = list(long = -122.259558, lat = 37.974515)
)

leaflet() %>%
  addTiles() %>% 
  addRectangles(
    lng1 = bbox2$p1$long, lat1 = bbox2$p1$lat,
    lng2 = bbox2$p2$long, lat2 = bbox2$p2$lat,
    fillColor = "transparent"
  ) %>%
  fitBounds(
    lng1 = bbox2$p1$long, lat1 = bbox2$p1$lat,
    lng2 = bbox2$p2$long, lat2 = bbox2$p2$lat,
  )

get_usgs_elevation_data(bbox2, size = image_size$size, file = "sf2.tif",
                        sr_bbox = 4326, sr_image = 4326)

elev_img <- raster::raster("sf2.tif")
elev_matrix <- matrix(
  raster::extract(elev_img, raster::extent(elev_img), buffer = 1000), 
  nrow = ncol(elev_img), ncol = nrow(elev_img)
)

ambmat <- ambient_shade(elev_matrix, zscale = 30)
raymat <- ray_shade(elev_matrix, zscale = 30, lambert = TRUE)
watermap <- detect_water(elev_matrix)
```

```{r, include = F, eval = F}
elev_matrix %>%
  sphere_shade(texture = "imhof4") %>%
  add_water(watermap, color = "imhof4") %>%
  add_shadow(raymat, max_darken = 0.5) %>%
  add_shadow(ambmat, max_darken = 0.5) %>%
  plot_map()

elev_matrix %>%
  sphere_shade(texture = "imhof4") %>%
  add_water(watermap, color = "imhof4") %>%
  add_shadow(raymat, max_darken = 0.5) %>%
  add_shadow(ambmat, max_darken = 0.5) %>%
  plot_3d(elev_matrix)

#render_snapshot()
```

```{r, include = F, eval = F}
montbay_water = montereybay

montbay_water[montbay_water < 0] = 0

montereybay %>%
 sphere_shade(texture="imhof4") %>%
 add_water(detect_water(montbay_water),color="imhof4") %>%
 plot_map()

montereybay %>% 
  sphere_shade() %>% 
  add_water(detect_water(montbay_water)) %>% 
  add_shadow(ray_shade(montereybay)) %>% 
  add_shadow(ambient_shade(montereybay)) %>% 
  plot_3d(montereybay, zscale = 50)
  plot_map()
```

```{r}
volcano %>% 
  sphere_shade() %>% 
  add_shadow(ray_shade(volcano)) %>% 
  add_shadow(ambient_shade(volcano)) %>% 
  plot_3d(volcano, zscale = 2)
```



## 20210304

Slacker

```{r}

```

## 20210305

```{r, include = F}
#file:///C:/Users/SimsCR/Downloads/zine_radial_patterns.pdf

lines  <-  tibble(
  x = seq(0, 19, by = .5),
  xend = x,
  y = c(rep(c(5, 10), 19), 5),
  yend = rep(0, 39),
  speed = 3)

dots  <-  lines %>%
select(x, y)
```

```{r}
ggplot() +
  geom_segment(data = lines,
               aes(x = x, y = y,xend = xend,yend = yend), color = "black") +
  geom_point(data = dots,
             aes(x = x, y = y), color = "blue") +
  scale_x_continuous(limits = c(0, 19)) +
  scale_y_continuous(limits = c(-5, 10)) +
  coord_polar() +
  theme_void()

```

## 20210308

gghighlight

```{r}

df <- datasets::swiss %>% 
  rownames_to_column(var = "Province")

df %>% ggplot(aes(Fertility, Catholic)) + 
  geom_point(color = "red") +
#  gghighlight(Fertility < 50, label_key = Province) + 
  gghighlight(Fertility > 82 & Catholic < 50, label_key = Province)
  


```

## 20210309

Tidy Tuesday - Bechdel Data

``````{r, include = F}

tt <- tt_load("2021-03-09")
readme(tt)

bech <- tt$raw_bechdel
movie <- tt$movies


all <- movie %>% left_join(bech)
```

```{r}
all %>% ggplot(aes(year, binary)) + 
  geom_jitter(shape = 1, color = "lightgreen") + 
  gghighlight(rating == 3, unhighlighted_params = aes(color = "black")) + 
  labs(y = "", x = "") +
  theme_bw()

```

```{r, include = F}
movie_clean <- movie %>%
  select(year, binary, budget, imdb_rating, genre) %>%  
  drop_na(genre, imdb_rating, binary)

min_max <- movie_clean %>%
  group_by(year, binary) %>%
  summarise(min = min(imdb_rating),
            max = max(imdb_rating),
            median = median(imdb_rating))


```


```{r}
ggplot(movie_clean, aes(x = year, y = imdb_rating, fill = binary, color = binary))+
  # geom_boxplot(aes(group = year), outlier.colour = "transparent", alpha = .4, color = "darkgrey") +
  geom_jitter(alpha = 0.15, size = 1, width = .15, show.legend = FALSE) +
  geom_segment(data = min_max, aes(x = year, y = min, xend = year, yend= max), color = "gray", size = 0.5, show.legend = FALSE)+
  geom_point(data =min_max, aes( x = year, y = min, color = binary), size = 2, color = "gray", show.legend = FALSE)+
  geom_point(data =min_max, aes( x = year, y = max, color = binary), size = 2, color = "gray", show.legend = FALSE)+
 
  ggbump::geom_bump(data = min_max, aes(x = year, y = median, color = binary), show.legend = FALSE)+

  scale_color_manual(values = c("#F26B38","#2F9599")) +
  #facet_wrap(.~binary, ncol = 2) +
  
  ylab("IMDB Rating") +
  xlab("")+
  
  labs(title = "Gender Bias in Movies Over Time",
       subtitle = "Median and Minimum/Maximum IMDB Ratings for Movies with <span style = 'color: #2F9599;'>**Passed**</span> and <span style = 'color: #F26B38;'>**Failed**</span> Test Results",
       caption = "Plot by **Tobias Stalder** | tobias-stalder.netlify.app<br>Data from **fivethirtyeight.com**<br>**#TidyTuesday**") +
  
  theme_minimal() +
  theme(plot.subtitle = element_markdown(),
        plot.caption = element_markdown(hjust = 0, lineheight = 1.5),
      text = element_text(family = "Segoe UI"),
      panel.grid.minor = element_blank(),
      strip.text = element_blank())
```

## 20210310

More Tidy Tuesday

```{r}
movie %>% 
  filter(!is.na(rated)) %>% 
  mutate(rated = fct_relevel(rated, levels = c("G", "PG","TV-PG", "PG-13","TV-14", "NC-17", "R", "X", "Unrated","Not Rated", "N/A"))) %>% 
  group_by(rated) %>% 
  summarize(n_movie = n(),
            pct_pass = mean(binary== "PASS")) %>% 
  ggplot(aes(rated, pct_pass)) + 
  geom_point()
```

## 20210311

terra

```{r, include = F}
p_load(terra)

x <- rast(ncol=36, nrow=18, xmin=-1000, xmax=1000, ymin=-100, ymax=900)
res(x)
res(x) <- 100

ncol(x) <- 18
crs(x) <- "+proj=utm +zone=48 +datum=WGS84"
x

r <- rast(ncol=10, nrow=10)
values(r) <- 1:ncell(r)

plot(r, main='Raster with 100 cells')
```

```{r}
filename <- system.file("ex/test.tif", package="terra")
filename
r <- rast(filename)
sources(r)
hasValues(r)
plot(r, main='SpatRaster from file')
```


```{r}
p_load(raster)


```


## 20210312

```{r}
library(raster)
library(rayshader)


raster1 = raster::raster("gebco_2020_n20.0_s1.0_w68.0_e92.0.tif")

plot(raster1, yaxt = 'n', xaxt = 'n', ann = F, bty =  'n')

```


## 20210315

India

```{r, eval = F}
library(raster)
library(rayshader)


#Load QGIS georeference image (see https://www.qgistutorials.com/en/docs/3/georeferencing_basics.html)
testindia = raster::stack("1870_southern-india_modified.tif") 

#Set bounding box for final map (cut off edges without data, introduced via reprojection)
india_bb = raster::extent(c(68,92,1,20))  # box size
cropped_india = raster::crop(testindia, india_bb)  # cropping

#Convert to RGB array
india_array = as.array(cropped_india)

#Load elevation data, sourced from GEBCO
raster1 = raster::raster("gebco_2020_n20.0_s1.0_w68.0_e92.0.tif")

#Reproject and crop elevation data to historical map coordinate system
reprojected_india = raster::projectRaster(raster1, crs=raster::crs(cropped_india))
cropped_reprojected_india = raster::crop(reprojected_india,india_bb)

#Reduce the size of the elevation data, for speed
small_india_matrix = resize_matrix(as.matrix(cropped_reprojected_india), scale = 0.2)

#Remove bathymetry data
water_india = small_india_matrix
water_india[is.na(water_india)] = 0
water_india[water_india < 0]=0
water_india = t(water_india)

#Compute shadows
ambient_layer = ambient_shade(water_india, zscale = 10, multicore = TRUE, maxsearch = 200)
ray_layer = ray_shade(water_india, zscale = 20, multicore = TRUE)

#Plot in 3D
(india_array/255) %>%
  add_shadow(ray_layer,0.3) %>%
  add_shadow(ambient_layer,0) %>%
  plot_3d(water_india,zscale=130)

#Render snapshot with depth of field
render_depth(focus=0.982,focallength = 4000)

#Plot in 2D
(india_array/255) %>%
  add_shadow(ray_layer,0.3) %>%
  add_shadow(ambient_layer,0) %>%
  plot_map()

%>% 
  ggsave(filename = "test.pdf", device = cairo_pdf, height = 20, width = 30)
```


## 20210316

Tidy Tuesday - Steam Games

```{r, include = F}
library(lubridate)

tt <- tt_load("2021-03-16")
readme(tt)

games <- tt$games %>% 
  mutate(peak_perc = parse_number(avg_peak_perc))

```

```{r, include = F}
test <- games %>% 
  filter(peak_perc > 0) %>% 
  filter(peak >= 10000) %>% 
  mutate(date_chr = paste0(year, ", ", month)) %>% 
  mutate(date = ymd(date_chr, truncated = 1)) %>% 
  dplyr::select(-month, -date_chr)
  

top50_1 <- test %>% 
  group_by(gamename) %>% 
  summarize(avg_players = mean(avg, na.rm = T)) %>% 
  arrange(desc(avg_players)) %>% 
  ungroup() %>% 
  slice(1:50)

top50 <- test %>% 
  filter(gamename %in% top50_1$gamename) %>% 
  left_join(top50_1)
```

``` {r}
top50 %>% 
  filter(avg_players > 50000) %>% 
  ggplot(aes(date, peak, color = gamename)) + 
  geom_point() + 
  scale_y_continuous("Peak Players", labels = comma) + 
  labs(x = "") + 
  theme(legend.position = "bottom", legend.title = element_blank())


```


## 20210317

Continue Tidy Tuesday

```{r}
fm <- test %>% 
  filter(str_detect(gamename, "Football Manager"))

fm %>% 
  ggplot(aes(date, peak, color = gamename)) + 
  geom_line() + 
  scale_y_continuous("Peak Players", labels = comma) + 
#  scale_x_continuous(breaks = c(2012, 2013, 2014, 2015, 2016, 2017, 2018, 2019, 2020, 2021)) + 
  labs(x = "") + 
#  geom_text(aes(label = gamename), check_overlap = T, show.legend = F) + 
  theme(legend.position = "bottom", legend.title = element_blank())
```


## 20210318

Open Street Maps Data. The plotting is slow.

```{r, include = F}
library(osmdata)

getbb("North Little Rock")

streets <- getbb("North Little Rock") %>% 
  opq() %>% 
  add_osm_feature(key = "highway", 
                  value = c("motorway", "primary", "secondary", "tertiary")) %>% 
  osmdata_sf()

small_streets <- getbb("North Little Rock")%>%
  opq()%>%
  add_osm_feature(key = "highway", 
                  value = c("residential", "living_street",
                            "unclassified",
                            "service", "footway")) %>%
  osmdata_sf()

river <- getbb("North Little Rock")%>%
  opq()%>%
  add_osm_feature(key = "waterway", value = "river") %>%
  osmdata_sf()
```

```{r, include = F}
NLR <- ggplot() +
  geom_sf(data = streets$osm_lines,
          inherit.aes = FALSE,
          color = "black",
          size = .4,
          alpha = .8) +
#  geom_sf(data = small_streets$osm_lines,
#          inherit.aes = FALSE,
#          color = "black",
#          size = .4,
#          alpha = .6) +
  geom_sf(data = river$osm_lines,
          inherit.aes = FALSE,
          color = "blue",
          size = 1,
          alpha = .5) +
  coord_sf(xlim = c(-92.40028, -92.09819), 
           ylim = c(34.67453, 34.87742),
           expand = FALSE)
```

```{r, echo = F, include = F, eval = F}
NLR
```



## 20210319

terrainr and progressr

```{r, include = F}
library(terrainr)
library(sf)
library(progressr)
library(raster)
library(osmdata)

handlers("progress")

simulated_data <- data.frame(id = seq(1, 100, 1),
                             lat = runif(100, 44.04905, 44.17609), 
                             lng = runif(100, -74.01188, -73.83493))

simulated_data <- st_as_sf(simulated_data, coords = c("lng", "lat"))
simulated_data <- st_set_crs(simulated_data, 4326)

with_progress( # Only needed if you're using progressr
  output_tiles <- get_tiles(simulated_data,
                            services = c("elevation", "ortho"),
                            resolution = 90 # pixel side length in meters
                            )
)
```

```{r, include = F}
raster::plot(raster::raster(output_tiles[["elevation"]][[1]]))

raster::plotRGB(raster::brick(output_tiles[["ortho"]][[1]]), scale = 1)

```

```{r}
sui <- data.frame(id = seq(1, 100, 1),
                             lat = runif(100, 47.5, 45.5), 
                             lng = runif(100, 5.6, 10.8))
  
test <- getbb("North Little Rock", format_out = "data.frame")
```

## 20210322

Trying cverdel's rayshader experiment

```{r, include = F}
p_load(rayshader, raster, rgl, rayrender)

#Load image
image_url<-"https://github.com/cverdel/rayshader_experiment/raw/main/Hermannsburg_map.tif"
temp<-tempfile()
download.file(image_url, temp, mode="wb")

rgb = raster::brick(temp)
raster::plotRGB(rgb, scale = 255)
dim(rgb)

#Load elevation data
DEM_url<-"https://github.com/cverdel/rayshader_experiment/raw/main/Hermannsburg_DEM.tif"
temp2<-tempfile()
download.file(DEM_url, temp2, mode="wb")

elevation1 = raster::raster(temp2)
res(elevation1) #Resolution of a pixel
extent(elevation1) #Extent of raster
dim(elevation1) #Dimensions of raster

elevation<-aggregate(elevation1,fact=1)
res(elevation) #Resolution of a pixel
extent(elevation) #Extent of raster
dim(elevation) #Dimensions of raster

height_shade(raster_to_matrix(elevation)) %>%
  plot_map()

#Splits image up into rgb
names(rgb) = c("r","g","b", "a")
rgb_r = rayshader::raster_to_matrix(rgb$r)
rgb_g = rayshader::raster_to_matrix(rgb$g)
rgb_b = rayshader::raster_to_matrix(rgb$b)
rgb

#Check CRS
raster::crs(rgb)
raster::crs(elevation)

#Raster to matrix
el_matrix = rayshader::raster_to_matrix(elevation)

map_array = array(0,dim=c(nrow(rgb_r),ncol(rgb_r),3))

map_array[,,1] = rgb_r/255 #Red 
map_array[,,2] = rgb_g/255 #Blue 
map_array[,,3] = rgb_b/255 #Green 
map_array = aperm(map_array, c(2,1,3))

plot_map(map_array)

#Reduce the size of the elevation data, for speed
small_el_matrix = reduce_matrix_size(el_matrix, scale = 1) #Numbers less than 1 reduce the size of the elevation data

#Resize map to match elevation
resized_overlay_file = paste0(tempfile(),".png")
grDevices::png(filename = resized_overlay_file, width = dim(small_el_matrix)[1], height = dim(small_el_matrix)[2])
par(mar = c(0,0,0,0))
plot(as.raster(map_array))
dev.off()
overlay_img = png::readPNG(resized_overlay_file)

zscale=30 #Larger number makes less vertical exaggeration

#Render
ambient_layer = ambient_shade(small_el_matrix, zscale = zscale, multicore = TRUE, maxsearch = 200)
ray_layer = ray_shade(small_el_matrix, zscale = zscale, multicore = TRUE)

rgl::rgl.close() #Closes the rgl window

#Plot in 3D
(overlay_img) %>%
  add_shadow(ray_layer,0.3) %>%
  add_shadow(ambient_layer,0) %>%
  plot_3d(small_el_matrix,zscale=zscale)
```



``` {r}
#Plot in 2D
(map_array) %>%
  add_shadow(ray_layer,0.3) %>%
  add_shadow(ambient_layer,0.3) %>%
  plot_map()

```

## 20210323

Tidy Tuesday - UN Votes

```{r, include = F}
tt <- tt_load("2021-03-23")
readme(tt)

library(unvotes)

votes <- tt$unvotes
issues <- tt$issues
roll <- tt$roll_calls

rm(tt)

all <- list(votes, issues, roll) %>% reduce(left_join)

```

```{r}
all %>% 
  ggplot(aes(issue, vote)) + 
  geom_count() + 
  coord_flip()
```

```{r}
all %>% 
  filter(country %in% c("United States", "Canada", "Mexico", "Russia", "China", "Japan"),
         !is.na(issue)) %>% 
  ggplot(aes(session, country, color = vote)) + 
  geom_jitter(width = 0.2, alpha = 0.5) + 
  scale_color_manual(values = c("gray90", "firebrick4", "palegreen4"), "Vote") + 
  facet_wrap(~issue) + 
  labs(y = "", x = "Session") + 
  theme(legend.position = "bottom")
```



## 20210324

ggbeeswarm

```{r, include = F}
library(ggbeeswarm)

mtcars %>% 
  ggplot(aes(as.factor(cyl), mpg)) + 
  geom_point()

mtcars %>% 
  ggplot(aes(as.factor(cyl), mpg)) + 
  geom_jitter(width = 0.1)

mtcars %>% 
  ggplot(aes(as.factor(cyl), mpg)) + 
  geom_beeswarm()

```

```{r}
all %>% 
  filter(country %in% c("United States", "Iraq", "Israel"),
         !is.na(issue)) %>% 
  ggplot(aes(session, country, color = vote)) + 
  geom_jitter(alpha = 0.5, width = 0.2) + 
  scale_color_manual(values = c("gray90", "firebrick4", "palegreen4"), "Vote") + 
  facet_wrap(~issue) + 
  labs(y = "", x = "Session") + 
  theme(legend.position = "bottom")

all %>% 
  filter(country %in% c("United States", "Iraq", "Israel"),
         !is.na(issue)) %>% 
  ggplot(aes(session, country, color = vote)) + 
  geom_beeswarm(alpha = 0.5, groupOnX = F, dodge.width = 0.2) + 
  scale_color_manual(values = c("gray90", "firebrick4", "palegreen4"), "Vote") + 
  facet_wrap(~issue) + 
  labs(y = "", x = "Session") + 
  theme(legend.position = "bottom")
```

## 20210325

ggforce and Palmer Penguins and hex colors

```{r, echo = F, include = F}
p_load(ggforce, palmerpenguins)

browseURL("https://ggforce.data-imaginist.com/reference/index.html")

browseURL("https://allisonhorst.github.io/palmerpenguins/")
```

```{r}
penguins %>% 
  filter(!is.na(sex)) %>% 
  ggplot(aes(flipper_length_mm, bill_length_mm, color = species)) + 
  geom_point() + 
  geom_mark_hull() +
  facet_wrap(~sex)

penguins %>% 
  filter(!is.na(sex)) %>% 
  ggplot(aes(flipper_length_mm, bill_length_mm, color = species)) + 
  geom_point() + 
  geom_smooth(method = "lm", se = F) +
  facet_zoom(x = species == "Gentoo") +
  labs(x = "Flipper Length (mm)", y = "Bill Length (mm)") + 
  theme(legend.position = "bottom") + 
  scale_color_manual("Species", values = c("#66ff00", "#ff9933", "#990000"))


```

## 20210326

Modeling with Palmer Penguins using broom

```{r, echo = F}
p_load(palmerpenguins)


pp_1 <- penguins %>% 
  lm(bill_length_mm ~ species + sex + flipper_length_mm + island, 
     data = .)

summary(pp_1)
tidy(pp_1)
vif(pp_1)
anova(pp_1)

penguins_2 <- augment(pp_1)

penguins_2 %>% 
  ggplot(aes(bill_length_mm, .fitted, color = species)) + 
  geom_point()

pp_2 <- penguins %>% 
  lm(bill_length_mm ~ species + sex + body_mass_g + island, 
     data = .)

summary(pp_2)
tidy(pp_2)
vif(pp_2)
anova(pp_2)


penguins_3 <- augment(pp_2)

penguins_3 %>% 
  ggplot(aes(bill_length_mm, .fitted, color = species)) + 
  geom_point()



```

## 20210329

penguins_raw and visdat

```{r echo = F}

p_load(palmerpenguins, lme4, emmeans)

p_raw <- penguins_raw %>% 
  clean_names()

length_lmer <- p_raw %>% lmer(culmen_length_mm ~ species + island + (1|individual_id), data = .)

tidy(length_lmer)
Anova(length_lmer)

#length_rg <- ref_grid(length_lmer)

#emmip(length_rg, body_mass_g ~ species)

```


```{r, echo = F}
p_load(visdat)

visdat::vis_dat(penguins)

penguins_4 <- penguins %>% 
  select_if(is.numeric) %>% 
  dplyr::select(-year)

visdat::vis_cor(penguins_4)
```

## 20210330

Tidy Tuesday

```{r, echo = F}
tt <- tt_load("2021-03-30")
readme(tt)

all_shades <- tt$allShades

all_shades <- all_shades %>% 
  mutate(brand_lump = fct_lump_min(brand, min = 150))

may <- all_shades %>% 
  filter(brand == "Maybelline")

(may_p <- may %>% 
  ggplot(aes(name, lightness, fill = name)) + 
  theme_void() + 
  geom_col(position = "fill") +
  scale_fill_manual(values = may$hex, labels = may$hex) +
  theme(legend.position = "none") + 
  facet_wrap(~product, scales = "free") + 
  labs(x = NULL, y = NULL)
)

ggplotly(may_p)

```

## 20210331

Just working on completing the month/knitting
```{r}

```



