---
title: "Daily R - October 2021"
output: html_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  fig.retina = 3,
  fig.path = here::here("exports", "October", "/"),
  out.width = "100%"
)

pacman::p_load(pacman, tidyverse, janitor, here, rio, job, skimr, paletteer, crsp)

theme_set(theme_bw(base_size = 15) + theme(legend.position = "bottom"))

```

# 20211001 - trying [{aRtsy}](https://koenderks.github.io/aRtsy/)

```{r}
p_load(aRtsy)


set.seed(1)
canvas_function(color = "navyblue")

set.seed(2)
canvas_polylines(colors = paletteer_d("palettetown::pikachu"))

set.seed(3)
canvas_squares(colors = paletteer_d("wesanderson::Zissou1"))


```


# 20211004 - [WIC Data](https://www.fns.usda.gov/pd/wic-program)

```{r, include = F}
p_load(polite, rvest)

# doesn't work
# session <- bow("https://www.fns.usda.gov/pd/wic-program")
# 
# wic_nodes <- scrape(session) %>% 
#   html_nodes("#main > div > div > div.l-constrain > div > div > div > section > table")
# 
# 
# wic_data <- wic_nodes %>% 
#   html_table() %>% 
#   flatten_df()
```

```{r, eval = F}
# doesn't work
pg <- read_html("https://www.fns.usda.gov/pd/wic-program")

# doesn't work
excel_links <- html_nodes(pg, xpath=".//a[contains(@href, '.xls')]") %>% 
  html_attr("href") %>% 
  sprintf("http://www.fns.usda.gov/pd/wic-program", .)

```

```{r, eval = F}
# doesn't work
test <- bow("https://www.fns.usda.gov/pd/wic-program") %>% 
  nod("https://www.fns.usda.gov/sites/default/files/resource-files/26wifypart-9.xls") %>% 
  rip() %>% 
  as.data.frame()
```

```{r}
# works

wic_files <- c("https://www.fns.usda.gov/sites/default/files/resource-files/26wifypart-9.xls",
               "https://www.fns.usda.gov/sites/default/files/resource-files/24wicfood$-9.xls",
               "https://www.fns.usda.gov/sites/default/files/resource-files/25wifyavgfd$-9.xls",
               "https://www.fns.usda.gov/sites/default/files/resource-files/23WICAdm$-9.xls")

#wic_data <- reduce(map(wic_files, ~import(.)), bind_rows)
```

# 20211005 - #TidyTuesday and Registered Nurses

```{r}
p_load(tidytuesdayR, usmap)

tt <- tt_load("2021-10-05")
readme(tt)


nurses <- tt$nurses %>% 
  clean_names()

skim(nurses)
```

```{r}
plot_usmap(regions = "states", data = nurses, values = "hourly_wage_avg") + 
  scale_fill_paletteer_c("harrypotter::ravenclaw") + 
  labs(fill =  "Mean Hourly Wage ($)") + 
  theme(legend.position = c(0.85, 0.02)) +
  facet_wrap(~year)
```


# 20211006 - Clean WIC data

```{r, eval = F}
states <- bind_cols(datasets::state.name, datasets::state.abb) %>% 
  rename(state = 1, abb = 2)

wic_raw <- map(wic_files, ~import(.))

clean_wic <- function(df, category){
  
  new_df <- df %>% 
    slice(-c(1, 3, 95, 96, 110, 111)) %>% 
    row_to_names(row_number = 1) %>% 
    clean_names() %>% 
    mutate(across(2:6, as.numeric)) %>% 
    mutate(division = case_when(state_indian_tribe %in% states$state ~ "State",
                              TRUE ~ "Tribe")) %>% 
    mutate(subdivision = case_when(division == "Tribe" & lag(division == "State") ~ lag(state_indian_tribe), 
                                   division == "Tribe" & lag(division == "Tribe") ~ lag(state_indian_tribe, 2),
#                                   division == "Tribe" & lag(division == "Tribe") & 
                                   TRUE ~ NA_character_))# %>%  # don't forget DC, Guam, Puerto Rico, Virgin Islands, Northern Marianas, etc.
    # pivot_longer(cols = 2:6) %>% 
    # rename(year = name) %>% 
    # separate(year, into = c("fy", "year"), sep = "_") %>% 
    # select(-fy) %>% 
    # mutate(year = as.numeric(year))

  
  names(new_df)[3] <- category
  
  return(new_df)
}

total <- wic_raw[[1]] %>% 
  clean_wic(category = "total_participation")

food_cost <- wic_raw[[2]] %>% 
  clean_wic(category = "food_cost")

avg_benefit <- wic_raw[[3]] %>% 
  clean_wic(category = "avg_benefit")

admin_cost <- wic_raw[[4]] %>% 
  clean_wic(category = "admin_cost")

all_wic <- list(total, food_cost, avg_benefit, admin_cost) %>% 
  reduce(left_join) %>% 
  mutate(division = case_when(state_indian_tribe %in% datasets::state.name ~ "State",
                              TRUE ~ "Tribe"))
```

# 20211007 - More Cleaning of the WIC Data

I need to figure out how to track their indentations.

I used `lag`, but I can't figure out how to make the `n` dynamically change based on the number of tribes within each state.

Moving on, because I don't feel passionate about this dataset.

```{r, eval = F}
# worked in previous day
```


# 20211008 - checking out [{groundhog}](https://groundhogr.com/)

{groundhog} lets you use packages based on a certain date. For example, if you ran your script on 2021-10-08 and you want the packages to be exactly the same (i.e. version number), you can use this package.

```{r, eval = F}
p_load(groundhog)

groundhog_day = "2021-10-08"  # date you want the packages to be from. Maybe date of last save or date of initiation.

# groundhog.library("package", groundhog_day)  # load packages as they were on `groundhog_day`
```


# 20211011 - trying [{tidymodels}](https://www.tidymodels.org/)

This week (except for Tuesday), I am going to work on the tidymodels framework.

```{r data import, include = F}
p_load(tidymodels, broom.mixed, dotwhisker, readr)

urchins <- read_csv("https://tidymodels.org/start/models/urchins.csv") %>% 
  setNames(c("food_regime", "initial_volume", "width")) %>% 
  mutate(food_regime = factor(food_regime, levels = c("Initial", "Low", "High")))
```

Plot of raw data.

```{r}
ggplot(urchins,
       aes(x = initial_volume, 
           y = width, 
           group = food_regime, 
           col = food_regime)) + 
  geom_point() + 
  geom_smooth(method = lm, se = FALSE) +
  scale_color_viridis_d(option = "plasma", end = .7)
```

```{r, include = F}
lm_mod <- linear_reg() %>% 
  set_engine("lm")

lm_fit <- lm_mod %>% 
  fit(width ~ initial_volume * food_regime, data = urchins)

lm_fit
```

Model summary (table and dot-whisker plot).

```{r}
tidy(lm_fit)

tidy(lm_fit) %>% 
  dwplot(dot_args = list(size = 2, color = "black"),
         whisker_args = list(color = "black"),
         vline = geom_vline(xintercept = 0, colour = "grey50", linetype = 2))

```

Predictions

```{r}
new_points <- expand.grid(initial_volume = 20,
                          food_regime = c("Initial", "Low", "High"))

mean_pred <- predict(lm_fit, new_data = new_points)

conf_int_pred <- predict(lm_fit,
                         new_data = new_points,
                         type = "conf_int")

plot_data <- new_points %>% 
  bind_cols(mean_pred) %>% 
  bind_cols(conf_int_pred)
```

Plot of predictions

```{r}
ggplot(plot_data, aes(x = food_regime)) + 
  geom_point(aes(y = .pred)) + 
  geom_errorbar(aes(ymin = .pred_lower,
                    ymax = .pred_upper),
                width = 0.2) + 
  labs(y = "urchin size")
```

# 20211012 - #TidyTuesday and Seafood Production

```{r, include = F}
p_load(tidytuesdayR, countrycode)

tt <- tt_load("2021-10-12")
readme(tt)

fish <- tt %>% 
  reduce(left_join) %>% 
  rename(pelagic_fish = 14, crustaceans = 15, cephalopods = 16, demersal_fish = 17,
         freshwater_fish = 18, molluscs = 19, other = 20) %>% 
  clean_names()

fish$continent <- countrycode(sourcevar = fish$entity,
                              origin = "country.name",
                              destination = "continent")

fish_sum <- fish %>% 
  select(continent, year, 14:20) %>% 
  filter(!is.na(continent)) %>% 
  group_by(continent, year) %>% 
  summarize(across(everything(), sum, na.rm = T)) %>% 
  pivot_longer(cols = 3:9) %>% 
  rename(fish_type = name, production = value)

```

```{r}
fish_sum %>% 
  ggplot(aes(year, production, color = fish_type)) + 
  geom_point() + 
  scale_color_paletteer_d("ggthemes::few_Dark") + 
  scale_y_continuous(labels = scales::comma_format()) + 
  facet_wrap(~ continent) + 
  theme(legend.position = c(0.8, 0.22))
```



# 20211013 - More {tidymodels} - [{recipes}](https://www.tidymodels.org/start/recipes/)

```{r, include = FALSE}
p_load(nycflights13)

set.seed(123)

flight_data <- 
  flights %>% 
  mutate(
    # Convert the arrival delay to a factor
    arr_delay = ifelse(arr_delay >= 30, "late", "on_time"),
    arr_delay = factor(arr_delay),
    # We will use the date (not date-time) in the recipe below
    date = lubridate::as_date(time_hour)
  ) %>% 
  # Include the weather data
  inner_join(weather, by = c("origin", "time_hour")) %>% 
  # Only retain the specific columns we will use
  select(dep_time, flight, origin, dest, air_time, distance, 
         carrier, date, arr_delay, time_hour) %>% 
  # Exclude missing data
  na.omit() %>% 
  # For creating models, it is better to have qualitative columns
  # encoded as factors (instead of character strings)
  mutate_if(is.character, as.factor)

flight_data %>% 
  count(arr_delay) %>% 
  mutate(prop = n/sum(n))

```

```{r, include = FALSE}

set.seed(222)
# Put 3/4 of the data into the training set 
data_split <- initial_split(flight_data, prop = 3/4)

# Create data frames for the two sets:
train_data <- training(data_split)
test_data  <- testing(data_split)

```

```{r, include = FALSE}
flights_rec <- 
  recipe(arr_delay ~ ., data = train_data)  %>%  # set model formula and data set
  update_role(flight, time_hour, new_role = "ID")  # update flight and time hour so they won't be used in models

summary(flights_rec)

flights_rec <- 
  recipe(arr_delay ~ ., data = train_data) %>% 
  update_role(flight, time_hour, new_role = "ID") %>% 
  step_date(date, features = c("dow", "month")) %>%  # gets day of week and the month
  step_holiday(date, 
               holidays = timeDate::listHolidays("US"),  # adds holidays
               keep_original_cols = FALSE) %>% 
  step_dummy(all_nominal_predictors())  # make dummy variables


# looking if any dest are only in train_data
test_data %>% 
  distinct(dest) %>% 
  anti_join(train_data)

flights_rec <- 
  recipe(arr_delay ~ ., data = train_data) %>% 
  update_role(flight, time_hour, new_role = "ID") %>% 
  step_date(date, features = c("dow", "month")) %>%               
  step_holiday(date, 
               holidays = timeDate::listHolidays("US"), 
               keep_original_cols = FALSE) %>% 
  step_dummy(all_nominal_predictors()) %>% 
  step_zv(all_predictors()) # removes zero variance columns (like LEX), ONLY PUT AFTER step_dummy()

```



```{r, include = FALSE}

# build model specification

lr_mod <- logistic_reg() %>% 
  set_engine("glm")


# build workflow
flights_wflow <- 
  workflow() %>% 
  add_model(lr_mod) %>% 
  add_recipe(flights_rec)

flights_wflow

# fit on training data

flights_fit <- 
  flights_wflow %>% 
  fit(data = train_data)


# extract model info

# flights_fit %>% 
#   extract_fit_parsnip() %>% 
#   tidy()


# predict arrival of test_data based on training_data

flights_aug <- 
  augment(flights_fit, test_data)
```

```{r}
# ROC from {yardstick} (included in tidymodels)

flights_aug %>% 
  roc_curve(truth = arr_delay, .pred_late) %>% 
  autoplot()

flights_aug %>% 
  roc_auc(truth = arr_delay, .pred_late)

```

Not too bad! We leave it to the reader to test out this workflow without this recipe. You can use `workflows::add_formula(arr_delay ~ .)` instead of `add_recipe()` (remember to remove the identification variables first!), and see whether our recipe improved our model’s ability to predict late arrivals.

`remove_formula`

# 20211014 - More {tidymodels} - [{resampling}](https://www.tidymodels.org/start/resampling/)

```{r cell-data-setup, include = FALSE}
p_load(tidymodels, modeldata, ranger)

data(cells, package = "modeldata")

cells %>% 
  count(class) %>% 
  mutate(prop = n/sum(n))

set.seed(123)

cell_split <- initial_split(cells %>% select(-case), 
                            strata = class)  # so that WS and PS have same proportion in splits

cell_train <- training(cell_split)
cell_test  <- testing(cell_split)

nrow(cell_train)

nrow(cell_train)/nrow(cells)


# training set proportions by class
cell_train %>% 
  count(class) %>% 
  mutate(prop = n/sum(n))

# test set proportions by class
cell_test %>% 
  count(class) %>% 
  mutate(prop = n/sum(n))


rf_mod <- 
  rand_forest(trees = 1000) %>% 
  set_engine("ranger") %>% 
  set_mode("classification")


set.seed(234)

rf_fit <- 
  rf_mod %>% 
  fit(class ~ ., data = cell_train)
rf_fit

```

```{r training-roc}
# ROC with training set
# not a good idea 
rf_training_pred <- 
  predict(rf_fit, cell_train) %>% 
  bind_cols(predict(rf_fit, cell_train, type = "prob")) %>% 
  # Add the true outcome data back in
  bind_cols(cell_train %>% 
              select(class))

rf_training_pred %>%                # training set predictions
  roc_auc(truth = class, .pred_PS)

rf_training_pred %>%                # training set predictions
  accuracy(truth = class, .pred_class)

# The model essentially memorizes the training set, resulting in unrealistic accuracy

```

```{r test-roc}
# ROC with test set

rf_testing_pred <- 
  predict(rf_fit, cell_test) %>% 
  bind_cols(predict(rf_fit, cell_test, type = "prob")) %>% 
  bind_cols(cell_test %>% select(class))


rf_testing_pred %>%                   # test set predictions
  roc_auc(truth = class, .pred_PS)

rf_testing_pred %>%                   # test set predictions
  accuracy(truth = class, .pred_class)


```

```{r resampling}
set.seed(345)

folds <- vfold_cv(cell_train, v = 10)
folds

rf_wf <- 
  workflow() %>%
  add_model(rf_mod) %>%
  add_formula(class ~ .)

set.seed(456)

rf_fit_rs <- 
  rf_wf %>% 
  fit_resamples(folds)

rf_fit_rs

collect_metrics(rf_fit_rs)
```

# 20211015 - More {tidymodels} - [{tuning}](https://www.tidymodels.org/start/tuning/)

```{r data prep, include = FALSE}
p_load(tidymodels, rpart.plot, vip)

data(cells, package = "modeldata")

set.seed(123)

cell_split <- initial_split(cells %>% select(-case), 
                            strata = class)
cell_train <- training(cell_split)
cell_test  <- testing(cell_split)

```

```{r tuning, include = FALSE}
tune_spec <- decision_tree(
  cost_complexity = tune(),
  tree_dept = tune()
) %>% 
  set_engine("rpart") %>% 
  set_mode("classification")

tree_grid <- grid_regular(cost_complexity(),
                          tree_depth(),
                          levels = 5)

set.seed(234)

cell_folds <- vfold_cv(cell_train)

set.seed(345)

tree_wf <- workflow() %>% 
  add_model(tune_spec) %>% 
  add_formula(class ~ .)

tree_res <- tree_wf %>% 
  tune_grid(
    resamples = cell_folds,
    grid = tree_grid
  )

tree_res

tree_res %>% 
  collect_metrics()
```

```{r results plot, include = TRUE}
tree_res %>%
  collect_metrics() %>%
  mutate(tree_depth = factor(tree_depth)) %>%
  ggplot(aes(cost_complexity, mean, color = tree_depth)) +
  geom_line(size = 1.5, alpha = 0.6) +
  geom_point(size = 2) +
  facet_wrap(~ .metric, scales = "free", nrow = 2) +
  scale_x_log10(labels = scales::label_number()) +
  scale_color_viridis_d(option = "plasma", begin = .9, end = 0)

```

```{r best, include = FALSE}
tree_res %>%
  show_best("accuracy")

best_tree <- tree_res %>%
  select_best("accuracy")

best_tree
```

```{r final-wf, include = F}
final_wf <- 
  tree_wf %>% 
  finalize_workflow(best_tree)
```

```{r final-fit, include = TRUE}
final_fit <- 
  final_wf %>%
  last_fit(cell_split) 

final_fit %>%
  collect_metrics()

final_fit %>%
  collect_predictions() %>% 
  roc_curve(class, .pred_PS) %>% 
  autoplot()

final_tree <- extract_workflow(final_fit)

final_tree %>%
  extract_fit_engine() %>%
  rpart.plot(roundint = FALSE)

final_tree %>% 
  extract_fit_parsnip() %>% 
  vip()

```
# 20211018 - More {tidymodels} - [{case study - part 1}](https://www.tidymodels.org/start/case-study/)

```{r case-study-setup, include = F}
p_load(tidymodels, vip)

hotels <- 
  read_csv('https://tidymodels.org/start/case-study/hotels.csv') %>%
  mutate_if(is.character, as.factor) 

hotels %>% 
  count(children) %>% 
  mutate(prop = n/sum(n))

set.seed(123)

splits      <- initial_split(hotels, strata = children)

hotel_other <- training(splits)
hotel_test  <- testing(splits)

set.seed(234)

val_set <- validation_split(hotel_other, 
                            strata = children, 
                            prop = 0.80)
```

```{r model-setup, include = F}
lr_mod <- 
  logistic_reg(penalty = tune(), mixture = 1) %>% 
  set_engine("glmnet")

holidays <- c("AllSouls", "AshWednesday", "ChristmasEve", "Easter", 
              "ChristmasDay", "GoodFriday", "NewYearsDay", "PalmSunday")

lr_recipe <- 
  recipe(children ~ ., data = hotel_other) %>%  # model formula and data
  step_date(arrival_date) %>%  # make predictors for year, month, and day of week
step_holiday(arrival_date, holidays = holidays) %>%  # specify holidays
  step_rm(arrival_date) %>%  # remove old date column
  step_dummy(all_nominal(), -all_outcomes()) %>% #create dummy variables for categorical
  step_zv(all_predictors()) %>% # remove zero variance
  step_normalize(all_predictors()) # center and scale all predictors

lr_workflow <- 
  workflow() %>% 
  add_model(lr_mod) %>% 
  add_recipe(lr_recipe)

lr_reg_grid <- tibble(penalty = 10^seq(-4, -1, length.out = 30))


```

```{r train-model, include = TRUE}
lr_res <- 
  lr_workflow %>% 
  tune_grid(val_set,
            grid = lr_reg_grid,
            control = control_grid(save_pred = TRUE),
            metrics = metric_set(roc_auc))

lr_plot <- 
  lr_res %>% 
  collect_metrics() %>% 
  ggplot(aes(x = penalty, y = mean)) + 
  geom_point() + 
  geom_line() + 
  ylab("Area under the ROC Curve") +
  scale_x_log10(labels = scales::label_number())

lr_plot 

lr_best <- 
  lr_res %>% 
  collect_metrics() %>% 
  arrange(penalty) %>% 
  slice(12)

lr_best

lr_auc <- 
  lr_res %>% 
  collect_predictions(parameters = lr_best) %>% 
  roc_curve(children, .pred_children) %>% 
  mutate(model = "Logistic Regression")

autoplot(lr_auc)

```
# 20211019 - #TidyTuesday and Pumpkins

```{r pumpkin-data, include = F}
p_load(tidytuesdayR)

tt <- tt_load("2021-10-19")
readme(tt)

pumpkins_raw <- tt$pumpkins

types <- tibble(
  category = c("Field Pumpkin", "Giant Pumpkin", "Giant Squash", "Giant Watermelon", "Long Gourd", "Tomato"),
  type = c("F", "P", "S", "W", "L", "T")
)

pumpkins <- pumpkins_raw  %>% 
  separate(id, into = c("year", "type"), sep = "-") %>% 
  left_join(types) %>% 
  mutate(across(c(weight_lbs, ott, est_weight), .fns = as.numeric))

skim(pumpkins)
```

```{r pumpkin-plots-1, include = TRUE}
pumpkins %>% 
  filter(ott > 0) %>% 
  ggplot(aes(ott, weight_lbs)) + 
  geom_point(alpha = 0.2) +
  geom_smooth(method = "lm", formula = y ~ poly(x, 2), se = F, color = "red") +
  facet_wrap(~category, scales = "free")

```

```{r yearly-winner, include = TRUE}
pumpkins_sum <- pumpkins %>% 
  group_by(year, category) %>% 
  summarize(winner = max(weight_lbs, na.rm = T))

pumpkins_sum %>% 
  ggplot(aes(year, winner, color = category)) + 
  geom_line(aes(group = category)) + 
  geom_point(shape = 21, aes(fill = category), color = "white", stroke = 1.5, size = 3) +
  scale_color_paletteer_d("ggpomological::pomological_palette", direction = -1) + 
  scale_fill_paletteer_d("ggpomological::pomological_palette", direction = -1)
```
# 20211020 - More {tidymodels} - [{case study - part 2}](https://www.tidymodels.org/start/case-study/)

```{r rf-model-setup-2, include = FALSE}
p_load(tidymodels)

cores <- parallel::detectCores()
cores

rf_mod <- 
  rand_forest(mtry = tune(), min_n = tune(), trees = 1000) %>% 
  set_engine("ranger", num.threads = cores) %>%  # usually let {tune} do the parallel processing
  set_mode("classification")

rf_recipe <- 
  recipe(children ~ ., data = hotel_other) %>% 
  step_date(arrival_date) %>% 
  step_holiday(arrival_date) %>% 
  step_rm(arrival_date) 

rf_workflow <- 
  workflow() %>% 
  add_model(rf_mod) %>% 
  add_recipe(rf_recipe)

set.seed(345)

rf_res <- 
  rf_workflow %>% 
  tune_grid(val_set,
            grid = 25,
            control = control_grid(save_pred = TRUE),
            metrics = metric_set(roc_auc))

rf_res %>% 
  show_best(metric = "roc_auc")
```

```{r rf_plot, include = TRUE}
autoplot(rf_res)
```

```{r best-rf, include = FALSE}
rf_best <- 
  rf_res %>% 
  select_best(metric = "roc_auc")
rf_best
```

```{r rf_auc, include = TRUE}
rf_auc <- 
  rf_res %>% 
  collect_predictions(parameters = rf_best) %>% 
  roc_curve(children, .pred_children) %>% 
  mutate(model = "Random Forest")

bind_rows(rf_auc, lr_auc) %>% 
  ggplot(aes(x = 1 - specificity, y = sensitivity, col = model)) + 
  geom_path(lwd = 1.5, alpha = 0.8) +
  geom_abline(lty = 3) + 
  coord_equal() + 
  scale_color_viridis_d(option = "plasma", end = .6)
```

# 20211021 - More {tidymodels} - [{case study - part 3}](https://www.tidymodels.org/start/case-study/)

```{r part-3, include = FALSE}
p_load(tidymodels)

last_rf_mod <- 
  rand_forest(mtry = 8, min_n = 7, trees = 1000) %>% 
  set_engine("ranger", num.threads = cores, importance = "impurity") %>% 
  set_mode("classification")

last_rf_workflow <- 
  rf_workflow %>% 
  update_model(last_rf_mod)

set.seed(345)

last_rf_fit <- 
  last_rf_workflow %>% 
  last_fit(splits)

last_rf_fit %>% 
  collect_metrics()
```

```{r part-3-vip, include = TRUE}
last_rf_fit %>% 
  pluck(".workflow", 1) %>% 
  extract_fit_parsnip() %>% 
  vip(num_features = 20)

last_rf_fit %>% 
  collect_predictions() %>% 
  roc_curve(children, .pred_children) %>% 
  autoplot()
```

# 20211022 - trying [{biscale}](https://slu-opengis.github.io/biscale/articles/biscale.html)

```{r biscale-setup, include = FALSE}
p_load(sf, biscale, cowplot)

data <- bi_class(stl_race_income, x = pctWhite, y = medInc, style = "quantile", dim = 3)
```

## V1

```{r biscale-plot-1, include = TRUE, fig.cap = "St. Louis - Biscale Map V1"}
(map <- ggplot() +
  geom_sf(data = data, mapping = aes(fill = bi_class), color = "white", size = 0.1, show.legend = FALSE) +
  bi_scale_fill(pal = "DkBlue", dim = 3) +
  labs(
    title = "Race and Income in St. Louis, MO",
    subtitle = "Dark Blue (DkBlue) Palette"
  ) +
  bi_theme() +
  theme(title = element_text(size = 10))
)
```

```{r biscale-plot-2, include = TRUE, fig.cap = "St. Louis - Biscale Map V2"}
legend <- bi_legend(pal = "DkBlue",
                    dim = 3,
                    xlab = "Higher % White ",
                    ylab = "Higher Income ",
                    size = 8)

# combine map with legend
(finalPlot <- ggdraw() +
  draw_plot(map, 0, 0, 1, 1) +
  draw_plot(legend, 0.2, .65, 0.2, 0.2)
)
```

## V2

```{r biscale-plot-3, include = TRUE, fig.cap = "St. Louis - Biscale Map V3"}
data2 <- bi_class(stl_race_income, x = pctWhite, y = medInc, style = "equal", dim = 3)


(map2 <- ggplot() +
  geom_sf(data = data2, mapping = aes(fill = bi_class), color = "white", size = 0.1, show.legend = FALSE) +
  bi_scale_fill(pal = "DkCyan", dim = 3) +
  labs(
    title = "Race and Income in St. Louis, MO",
    subtitle = "Dark Blue (DkBlue) Palette"
  ) +
  bi_theme() +
  theme(title = element_text(size = 10))
)
```

```{r biscale-plot-4, include = TRUE, fig.cap = "St. Louis - Biscale Map V4"}
legend2 <- bi_legend(pal = "DkCyan",
                    dim = 3,
                    xlab = "Higher % White ",
                    ylab = "Higher Income ",
                    size = 8)

# combine map with legend
(finalPlot2 <- ggdraw() +
  draw_plot(map2, 0, 0, 1, 1) +
  draw_plot(legend2, 0.2, .65, 0.2, 0.2)
)

```

I think this is cool. I'll be on the lookout for data that I could use in the future.

# 20211025 - trying [{ggdag}](https://cran.r-project.org/web/packages/ggdag/vignettes/intro-to-ggdag.html)

```{r ggdag-setup, include = T}
p_load(dagitty, ggdag)

bigger_dag <- dagify(y ~ x + a + b,
                     x ~ a + b,
                     exposure = "x",
                     outcome = "y")

dag_paths(bigger_dag)

bigger_dag %>% 
  dag_paths() %>%
  group_by(set) %>%
  filter(!is.na(path) & !is.na(name)) %>% 
  summarize(n_vars_between = n() - 1)

```

```{r ggdat-plots-1, include = T}
ggdag_paths(bigger_dag) + theme_void()

ggdag_parents(bigger_dag, "x") + theme_void()
```

```{r ggdat-ggplot, include = T}
bigger_dag %>% 
  node_parents("x") %>% 
  ggplot(aes(x = x, y = y, xend = xend, yend = yend, color = parent)) +
      geom_dag_point() +
      geom_dag_edges_diagonal() +
      geom_dag_text(col = "white") +
      theme_dag() +
      scale_color_manual(values = c("#F87050FF", "#7870B0FF"), breaks  = c("parent", "child"))



```





# 20211026 - #TidyTuesday and Trail Running

```{r trail-setup, include = FALSE, eval = F}
p_load(tidytuesdayR, RCurl)

tt <- tt_load(2021, week = 44)

```

```{r trail-data, include = F}
race_raw <- import(here("data", "tt_wk44.xlsx"), which = "race")

ultra_rankings_raw <- import(here("data", "tt_wk44.xlsx"), which = "ultra_rankings")

skim(race_raw)

skim(ultra_rankings_raw)

race <- race %>% 
  mutate(country = case_when(str_detect(country, "United States") ~ "United States", 
                             TRUE ~ country))
```

```{r race-country, include = T}
# race %>% 
#   count(city, country)

race %>% 
  count(country) %>% 
  arrange(desc(n)) %>% 
  mutate(country = fct_reorder(country, n)) %>% 
  slice(1:15) %>% 
  ggplot(aes(reorder(country, n), n)) + 
  geom_segment(aes(x = country, xend = country, y = n, yend = 0)) +
  geom_point() + 
  coord_flip() + 
  labs(x = NULL, y = "Number of Ultra-Marathons")
```


# Ideas


template, rprojroot, rgbif, geoviz, ggmap, rayvista, camcorder, {renv}, {rayvertex}, {labelled}, {hrbrthemes}, {firatheme}, {pwr}, voronoi, {reprex}, {ggdag}, debug = T for geom_text, {lcmm}, {rolldown}, {ggperiodic}, {codebook}, {muvr}, {pcalg}, {packagemetrics}, {steveproj}, {ungeviz}, {themis}, {biscale}, {prettydoc}


<https://albert-rapp.de/post/2021-09-16-similar-data-and-list-like-columns/#helpful-concepts>

<https://www.swisstopo.admin.ch/>

<https://www.ign.es/web/ign/portal/cbg-area-cartografia>

<http://shadedrelief.com/SampleElevationModels/>

<https://www.neonscience.org/resources/learning-hub/tutorials>

<https://docs.ropensci.org/rgbif/articles/rgbif.html>

<https://ryo-n7.github.io/2020-05-14-webscrape-soccer-data-with-R/>

<https://github.com/gkaramanis/aRt/blob/master/split-bar/split-bar.R>

<https://www.tidymodels.org/>

<https://rstudio.github.io/distill/basics.html>

<https://github.com/thebioengineer/camcorder>

<https://gist.github.com/Worville/c4149ece45a75928a404d316151ba0fe>


```{r, eval = F}
library(ezknitr)

ezknit(file = "October 2021.Rmd", out_dir = "html files", fig_dir = "exports/October", keep_md = F)
```

