---
title: "Daily R - October 2021"
output: html_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  fig.retina = 3,
  fig.path = here::here("exports", "October", "/")
)

pacman::p_load(pacman, tidyverse, janitor, here, rio, job, skimr, paletteer)

theme_set(theme_bw(base_size = 15))

```

# 20211001 - trying [{aRtsy}](https://koenderks.github.io/aRtsy/)

```{r}
p_load(aRtsy)


set.seed(1)
canvas_function(color = "navyblue")

set.seed(2)
canvas_polylines(colors = paletteer_d("palettetown::pikachu"))

set.seed(3)
canvas_squares(colors = paletteer_d("wesanderson::Zissou1"))


```


# 20211002 - [WIC Data](https://www.fns.usda.gov/pd/wic-program) and [{polite}](https://dmi3kno.github.io/polite/)


# Ideas

template, tidymodels, groundhog, ezknitr, rprojroot, rgbif, polite (web scraping), geoviz, ggmap, rayvista, circlize, camcorder, {renv}, {rayvertex}, {labelled}, {report}, {insight}, {performance}, {parameters}, {correlation}, {easystats}, {hrbrthemes}, {firatheme}, {pwr}, voronoi, {reprex}, {ggdag}, {aRtsy}, debug = T for geom_text, {lcmm}, {rolldown}, {ggperiodic}, {codebook}, {muvr}, {pcalg}, {packagemetrics}, {steveproj}


<https://albert-rapp.de/post/2021-09-16-similar-data-and-list-like-columns/#helpful-concepts>

<https://www.swisstopo.admin.ch/>

<https://www.ign.es/web/ign/portal/cbg-area-cartografia>

<http://shadedrelief.com/SampleElevationModels/>

<https://www.neonscience.org/resources/learning-hub/tutorials>

<https://docs.ropensci.org/rgbif/articles/rgbif.html>

<https://ryo-n7.github.io/2020-05-14-webscrape-soccer-data-with-R/>

<https://github.com/gkaramanis/aRt/blob/master/split-bar/split-bar.R>

<https://www.tidymodels.org/>

<https://rstudio.github.io/distill/basics.html>

<https://github.com/thebioengineer/camcorder>

<https://gist.github.com/Worville/c4149ece45a75928a404d316151ba0fe>