---
title: "Daily R - October 2021"
output: html_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  fig.retina = 3,
  fig.path = here::here("exports", "October", "/"),
  out.width = "100%"
)

pacman::p_load(pacman, tidyverse, janitor, here, rio, job, skimr, paletteer)

theme_set(theme_bw(base_size = 15))

```

# 20211001 - trying [{aRtsy}](https://koenderks.github.io/aRtsy/)

```{r}
p_load(aRtsy)


set.seed(1)
canvas_function(color = "navyblue")

set.seed(2)
canvas_polylines(colors = paletteer_d("palettetown::pikachu"))

set.seed(3)
canvas_squares(colors = paletteer_d("wesanderson::Zissou1"))


```


# 20211004 - [WIC Data](https://www.fns.usda.gov/pd/wic-program)

```{r, include = F}
p_load(polite, rvest)

# doesn't work
# session <- bow("https://www.fns.usda.gov/pd/wic-program")
# 
# wic_nodes <- scrape(session) %>% 
#   html_nodes("#main > div > div > div.l-constrain > div > div > div > section > table")
# 
# 
# wic_data <- wic_nodes %>% 
#   html_table() %>% 
#   flatten_df()
```

```{r, eval = F}
# doesn't work
pg <- read_html("https://www.fns.usda.gov/pd/wic-program")

# doesn't work
excel_links <- html_nodes(pg, xpath=".//a[contains(@href, '.xls')]") %>% 
  html_attr("href") %>% 
  sprintf("http://www.fns.usda.gov/pd/wic-program", .)

```

```{r, eval = F}
# doesn't work
test <- bow("https://www.fns.usda.gov/pd/wic-program") %>% 
  nod("https://www.fns.usda.gov/sites/default/files/resource-files/26wifypart-9.xls") %>% 
  rip() %>% 
  as.data.frame()
```

```{r}
# works

wic_files <- c("https://www.fns.usda.gov/sites/default/files/resource-files/26wifypart-9.xls",
               "https://www.fns.usda.gov/sites/default/files/resource-files/24wicfood$-9.xls",
               "https://www.fns.usda.gov/sites/default/files/resource-files/25wifyavgfd$-9.xls",
               "https://www.fns.usda.gov/sites/default/files/resource-files/23WICAdm$-9.xls")

#wic_data <- reduce(map(wic_files, ~import(.)), bind_rows)
```

# 20211005 - #TidyTuesday and Registered Nurses

```{r}
p_load(tidytuesdayR, usmap)

tt <- tt_load("2021-10-05")
readme(tt)


nurses <- tt$nurses %>% 
  clean_names()

skim(nurses)
```

```{r}
plot_usmap(regions = "states", data = nurses, values = "hourly_wage_avg") + 
  scale_fill_paletteer_c("harrypotter::ravenclaw") + 
  labs(fill =  "Mean Hourly Wage ($)") + 
  theme(legend.position = c(0.85, 0.02)) +
  facet_wrap(~year)
```


# 20211006 - Clean WIC data

```{r}
wic_raw <- map(wic_files, ~import(.))

clean_wic <- function(df, category){
  
  new_df <- df %>% 
    slice(-c(1, 3, 95, 96, 110, 111)) %>% 
    row_to_names(row_number = 1) %>% 
    clean_names() %>% 
    mutate(across(2:6, as.numeric)) %>% 
    pivot_longer(cols = 2:6) %>% 
    rename(year = name) %>% 
    separate(year, into = c("fy", "year"), sep = "_") %>% 
    select(-fy) %>% 
    mutate(year = as.numeric(year))
  
  names(new_df)[3] <- category
  
  return(new_df)
}

total <- wic_raw[[1]] %>% 
  clean_wic(category = "total_participation")

food_cost <- wic_raw[[2]] %>% 
  clean_wic(category = "food_cost")

avg_benefit <- wic_raw[[3]] %>% 
  clean_wic(category = "avg_benefit")

admin_cost <- wic_raw[[4]] %>% 
  clean_wic(category = "admin_cost")

all_wic <- list(total, food_cost, avg_benefit, admin_cost) %>% 
  reduce(left_join)
```

# 20211006 - More Cleaning of the WIC Data

I need to figure out how to track their indentions.

```{r}

```


# Ideas

template, tidymodels, groundhog, ezknitr, rprojroot, rgbif, polite (web scraping), geoviz, ggmap, rayvista, circlize, camcorder, {renv}, {rayvertex}, {labelled}, {report}, {insight}, {performance}, {parameters}, {correlation}, {easystats}, {hrbrthemes}, {firatheme}, {pwr}, voronoi, {reprex}, {ggdag}, {aRtsy}, debug = T for geom_text, {lcmm}, {rolldown}, {ggperiodic}, {codebook}, {muvr}, {pcalg}, {packagemetrics}, {steveproj}


<https://albert-rapp.de/post/2021-09-16-similar-data-and-list-like-columns/#helpful-concepts>

<https://www.swisstopo.admin.ch/>

<https://www.ign.es/web/ign/portal/cbg-area-cartografia>

<http://shadedrelief.com/SampleElevationModels/>

<https://www.neonscience.org/resources/learning-hub/tutorials>

<https://docs.ropensci.org/rgbif/articles/rgbif.html>

<https://ryo-n7.github.io/2020-05-14-webscrape-soccer-data-with-R/>

<https://github.com/gkaramanis/aRt/blob/master/split-bar/split-bar.R>

<https://www.tidymodels.org/>

<https://rstudio.github.io/distill/basics.html>

<https://github.com/thebioengineer/camcorder>

<https://gist.github.com/Worville/c4149ece45a75928a404d316151ba0fe>